\chapter{Locomotion}

``\textit{...Of all recent developments in our society, nothing has been more influential than that of the Sail Train. These locomotives, first using coal-fires to heat the steam that drives them, were quickly redeveloped with the advent of Solar Sails.\\
Solar Sails enabled crystals of glass, peridot, and quartz to be charged with solar energy that, at the behest of an onboard Alchemist, would heat water that in turn would drive the piston.\\
The pistons driven in this way quickly outpaced those driven by steam heated by coal-power. The chief benefit was the elimination of coal, which allowed for a more streamlined engine design, fewer staff on hand to pilot the engine, and most importantly, lower pulmonary and injury risk to those staff remaining on board.\\
In the decade following S.R. 1232, each and every steam locomotive was fully replaced with a Sail Train counterpart...}"\\

- \textbf{As quoted from `Popular Incantates', Issue 45, Autumn of S.R. 1247}\\


\lettrine{The}{last week and a half} of Tiffany's life was a veritable roller-coaster.
Her preparations kept her busy well into the Twilight hours of each day, and the unending, ever-multiplying lists of tiny associated tasks that refused to shrink threatened to overwhelm her.
Tiffany doggedly grinned and bore the logistic strain. 
She would not allow the excitement of this once-in-a-lifetime opportunity to be dampened with the cares of ticket purchases, grocery pre-orders, and luggage.\\

Tiffany, who had prided herself in her minimal attitude toward possessions, was quite taken aback at the sheer volume of items that she had to either pack or have stored.
Her hostel room would be let to another student for the six to eight months she would spend in Valleyton, as was naturally the University's right.
Therefore, she needed to completely remove all personal effects from the hostel room or risk having them donated.
Luckily, she was able to send packages of important items too large to carry in her hand-luggage ahead to Valleyton, and those items she would not need she sent home to her mother in Mountainkeep.\\

Besides the luggage and storage, her days were also filled with constant correspondence.
Not wanting to spend precious time sourcing her own accommodation on top of everything else, she opted to stick with Proffessor Hewlwyn's recommended contact early on.
The contact, a woman called Osthryn, was friendly and helpful enough in their exchanges.
However, some inconsistencies in their communication soon revealed that a younger woman, Raine, was also writing Osthryn's letters of arrangement for her.
This was eventually stated upfront after the fourth or fifth letter that Tiffany felt read strangely.
The admission did not need any prompting from her side, which Tiffany chose to believe as a sign that the accomodation would be legitimate regardless of the initial strangeness.\\

Rowan, also, proved to be a surprising thorn in her side the last few days.
He was full of questions, comments, and concerns about her proposal. 
If she had not been so busy or focused on this trip to a career-defining location, she might have been flattered by this sudden uptick in attention.
Instead, she found herself unable to enjoy it -- her mind always too far elsewhere for Rowan to get a satisfactory answer, and for her in turn to fully appreciate his questions.
She determined, to his apparent relief or delight, that it would be best for them to exchange telepost addresses and continue these conversations once she was properly settled at Valleyton.\\

Professor Helwyn was especially helpful beyond project parameters, helping her navigate the complex processes surrounding approved Scope research.
There were opportunities for funding, and the University did already subsidise her accomodation with Osthryn, but she would need to rely on part-time work for her personal expenses.
She had expected this, but she was grateful to Professor Helwyn for his thorough explanation of the resources available to her.
She was, however, unsure that she would be able to gather all the data she would need before the six-month deadline.
She felt that Professor Helwyn was overeager for her results.\\

Between the hundred-and-one tasks, Osthryn/Raine's frequent letters, Rowan's pestering, and Professor Helwyn's ever-evolving expecations, Tiffany had no room for her own thoughts.
Now, as she stood waiting at Grosbergan station for her Sail Train that would take her to Valleyton, she was enveloped in a blessed cocoon of expectation that allowed her to feel her excitement fully.
She imagined to herself what Valleyton would be like, how it would feel to see and interact with the famed Scope finally, and visualised herself seeing and \textit{touching} a Glasswood tree in person.
These happy thoughts kept her company as she rocked back and forth on the balls of her feet, looking in the direction that the Sail Train would approach from.\\

The early morning light of Sol Primus shining through the mist bathed the station and tracks in a cozy blue haze.
Tiffany could just barely make out the time on the large station clock and the slowly increasing number of figures as passengers began filtering to the platform.
The platform was well-packed, but very few of those climbing on the train here would end their journey in Valleyton.
Those bound for Valleyton would take a connecting train at Rivermouth Station, where the rest would remain on this train scheduled to go directly to Mountainkeep.
Usually, Tiffany would have stayed on the train, but today, she needed to remember her transfer.
She ensured that she had both ticket stubs within easy reach.\\

A copy of her current pleasure-read, \textit{Anatomy of Draconic Folklore}, kept the ticket stubs company in one of the large under-skirt pockets tied around her waist, which she accessed through a slit in her overskirt.
The other pocket, to balance out the weight, held her little notebook and pen, along with a coin purse, some extra quartz crystals, and other sundry essentials.
Her satchel, for safety's sake, was neatly stowed within her small rolling suitcase. 
She carried nothing larger than it with her, preferring to have everything immediately valuable to her within easy reach of her person.
Small things, like keeping a whole book in her pocket as a ward against a long train ride, made her grateful for the continued availability of the older skirt style.
She preferred appearing a bit more vintage to embracing the newer silhouettes from Mountainkeep that aimed to reduce or eliminate the pocket altogether. 
The necessity of a reticule or satchel while traveling, beyond the inanely stupid ``pigeon chest" many of the newer busks and corsets created, would simply interfere with her too much for her own liking.\\

The characteristic grinding of steel-against-steel alerted her to the approach of the Sail Train.
It appeared through the mist far sooner than one would expect, the only noise coming from it the screech of the brakes and the friction of the wheels on the track.
This Sail Train, like many others still in operation that were retro-fitted from the original coal-fired steam locomotives, still held all the imposing bulk and presence of its predecessor.
The coal tender had been completely done away with. 
The firebox, no longer required, was broken out to expand the cab.
Instead of two persons each either shoveling coal or operating the controls, a single pilot now manned the cab.
The smokestacks, still intact, now had a spinning Solar Sail mounted on high, the smoke box now serving as housing for the crystals charged with the solar magic.\\

One by one the coach doors opened, the passengers embarking as the door closest to their position opened.
Tiffany was grateful that this train was starting in Grosbergan. 
An empty coach where she would not need to jostle for a good window seat with already-seated passengers was always welcome.
She chose a bench that faced the front of the coach, disliking the feeling of moving in reverse, and scooted in closest to the window. 
Her little rolling-case, secured with her foot, fit neatly under the table that she shared with a reverse-facing bench across from her.
A fashionable gentleman tipped his hat to her before removing it and placing on the table, as if to claim the spot. 
Quickly, he took up the bench facing her as the coach filled up with passengers, similarly aiming for a seat close to the window.\\

Tiffany met his eyes and, with a polite ``Good morning," leaned back against her backrest and stared out the window, waiting for the train's departure.
Despite the week's activity, she appeared far more whole and human than she did on that evening when she completed her amplifier.
Tiffany's resolve to come across as prepared and professional as possible when meeting her hosts for the first time shone through.
Her thick red hair, normally simply tied with a ribbon at the base of her neck, was now tightly pinned up in a neat arrangement of rolls.
Her characteristic curls only appeared in strategically placed, wispy coils framing her forehead.
She had gone through the trouble of applying some rouge and powder to her face, and while her defined cheekbones and deep-set eyes still betrayed her gaunt features, she appeared far less pale.\\

The red crystal between the two passengers sprang to life, shining brightly as a thin, lightly distorted voice emanated from the small phonograph cone on the table.\\

``\textit{Welcome to Sail Train 4432, en route to Mountainkeep, with a train-change stop for Valleyton passengers at Rivermouth Station. Please have your tickets ready for inspection, and remain seated until the ushers have passed you. All coach doors are locked upon departure. In the event of an emergency, coach doors will open themselves. Please take note of exits closest to you, and refrain from moving between coaches during any unplanned stop or emergency disembarkation.
Our estimated time of arrival at Rivermouth Station is eight hours. 
Thank you for choosing Primus Rail for your journey, and enjoy your travels."}\\

After a short wait, the train lurched forward, slowly building up speed once it had fully left Grosbergan Station and neared the open railroad.
Tiffany and her new travel companion both watched the landscape passing them by through the windows.
The rolling hills surrounding Grosbergan soon gave way to open plains with mountains on the horizon, a small forest nestled at the base.
Tiffany cast a glance at her fellow passenger, the latter already engrossed in a magazine.
She followed suit, removing her treasured copy of \textit{Anatomy of Draconic Folklore} from her pocket.
The usher passed by them, nodding in acknowledgement of her ticket stub to Rivermouth Station when she held it out to him.\\

The usher past now past her, her counterpart now otherwise engaged, and eight hours of open railroad in front of her, Tiffany got stuck into her book.\\

\begin{center}
    ***
\end{center}

``\textit{... The biggest difficulty in reconstructing a true picture of Dragons as they lived and breathed is not simply that they, like many other legendary beasts, are extinct. It is that this particular legendary beast was so mythologised; both in the time periods that they lived and in the centuries immediately following the last known sighting. Even with allowance for magic as we know it today, several aspects of Draconic Folklore are so far-fetched as to obscure any real patterns that we can glean from them.}\\

\textit{Normally, folklore can be loosely corroborated by contemporary spellbooks, clerical records, and historical accounts. Unfortunately, the reality is that much of the records and written folklore from the pre-rationalist period (pre-S.R. 516) were either lost or destroyed. What follows is that much of what we have to go on from period of circa S.R. 33 to S.R. 516 either does not exist, is partially complete, or is rewritten from a post-rationalist perspective. We have reason to believe that the oral tradition of the majority of the early Solus Recessus era's Draconic Folklore is faithful to the original interpretation, but much of the supporting information we would have relied on to interpret it is mostly lost.}\\

\textit{This is no cause for despair, however. While the loss of original spellbooks and some historical chronicles is a grave loss to many disciplines, Wizardry especially, we are still able to piece together a coherent idea of what Dragons might have been like. Chief among our hopes are the several sets of remains that have been discovered all over the continent. While not corresponding fully to many descriptions in folklore, the skeletons of these winged reptiles are unlikely to belong to any other creature.}\\

\textit{These remains show that Dragons were consistently far smaller in size than folklore holds to. Typically, a Dragon's skeleton is no larger than a moderately large horse, with a wingspan of 20 meters. While folklore varied between describing Dragons as both having forelegs in addition to their wings and not, the remains we have discovered all have a decisive lack of forelegs. Instead, the wings were integrated with the front limbs, utilizing the shoulder joints for flight.}\\

\textit{While these and many other differences were apparent, other evidence from both the excavation sites and the remains themselves lined up with several folk themes. For instance, the bones often showed signs of being nicked by sharp objects, indicating a violent death. Remains of weapons such as swords, arrows, and spears embedded in the Dragons' thoracic cavities seem to align with the many `noble knight' style stories. Other aspects of folklore, such as treasure-hoarding tendencies, were not apparent at the excavation sites themselves, but often some other artifacts of value were found previously in the area. This link is tenuous at best, but the reader is encouraged to imagine any manner of treasure-hoarding stories from their childhood if they so desire.}\\

\textit{What is not definitively clear is whether Dragons were truly fire-breathing creatures. Many other graves excavated in areas surrounding the Dragons' remains did yield bones with evidence of scorch damage. What confounds this is that these graves, often mass graves, were also close to known historic battlefields where flaming arrows and other fire-based weapons were used in wars of old. The remains of the Dragons, likewise, were too decayed to sufficiently study soft tissues, rendering study from that angle useless.}..."\\

A cough and a jostle of the coach brought Tiffany to the surface. 
She looked up from her book to the clock hanging above the inter-coach door. 
Only twenty minutes to go until they reached Valleyton. 
She had changed trains at Rivermouth Station nearly two hours earlier. 
The second train had only two coaches, and they were sparsely populated.
She finally had a true comprehension of why the ticket for the second leg of her trip was so costly.
To maintain a line to such a removed location, even if the line was otherwise well-used during festival and holiday seasons, would be a tall ask at the general Sail Train rates.\\

The scenery across the Tansonbenoemderivier gradually shifted from grassy plains to sparse dots of temperate woodland.
Tall evergreen conifers grew denser and denser. 
Meadows carpeted with dense wild-flowers broke the tree line intermittently. 
Mountains enclosed the view when they reached the pass, and a short stretch through the tunnel brought Valleyton into full view below them.\\

Tiffany gasped at the sight. 
The paintings and postcards she had seen sometimes sported as souvenirs did not do the scene the hamlet painted justice.
The river emptied into a large, glassy lake. 
The still, blue waters contrasted with the bright green of the valley freshly in spring.
Quaint, whitewashed houses and cottages, alternating between bright-red tiled roofs and thatch, congregated in concentric circles around a central square.
Other smallholding and cottages spread out from the center, nestling into the foothills of the mountain or stretching to the lakeside.
The Glasswoods themselves surrounded the lake in a half-moon formation, the trees stretching from there back up the mountainside as far as they could go.\\

A little beyond the tree-line on the mountainside, in stark contrast to the hamlet scene, stood The Scope.
It was an impressively large building, with a green-patinaed copper dome that featured as its defining trait.
It looked massive from here, but Tiffany wondered how large it would truly be in person.
The dome consisted of sets of sliding panels, and various instruments dotted its surface.
From this angle, she could see that one of the segments had been pulled aside. 
Her eyes stretched in disbelief at the sight of a telescope that dwarfed her wildest imagination that appeared within the open space.
Crews were cleaning it now - the men hanging precariously from harnesses appeared as insects crawling on an eyeglass.\\

The Scope was out of view when the train slowed to a stop at the little Valleyton station. 
A single platform with a lonely bench kept the well-maintained but simple station-house company.
A young woman with dark brown hair casually flowing down to her shoulders sat cross-legged and at attention on the bench, fidgeting and swinging her leg impatiently as she watched the train come to a stop.
After a few moments, the coach doors slid open with the announcement to disembark. 
Tiffany replaced her book in her pocket, before removing her rolling case from the luggage net overhead.
The coaches to Valleyton did not have benches with tables, instead having rows of seats with overhead luggage storage.\\

Assuming the woman at the bench to be Raine, who had arranged to meet her at the station, Tiffany made her way over to her.
Raine stood, a bright, genuine smile gracing her face.\\
``You must be Tiffany? Oh, wonderful. I trust your train journey went well?"\\
Tiffany could scarcely muster a reply before Raine continued, ``Osthryn's cottage is at the Lakeshore just as the forest begins. It is quite a ways out of town," Raine took hold of Tiffany's rolling case handle as she began moving to the platform exit, Tiffany hastily following, ``I hope you don't mind a bit of a walk!"\\
``Oh, no, a good long walk after sitting still for so long would be wonderful," Tiffany responded, smiling, doing her best to keep up with the quick-paced Raine who had already descended the platform stairs and was making her way to the road with Tiffany's luggage in tow.\\

``Thank you for offering to carry my suitcase, but I don't mind carrying it myself." Tiffany started, reaching to take her suitcase back. 
Raine merely continued walking.\\
``Please, allow me. It is a pleasure to help" Raine insisted.\\
Tiffany saw no point in arguing, and allowing herself to start feeling her road-weariness, fell comfortably into step with Raine.\\
``Are you Osthryn's assistant? How are you related to her?" Tiffany started, trying to make conversation.\\

``Something like that," Raine responded, ``I work for her, but as a conservationist under the fund she is the benefactor of. The nature of the work means that I am constantly close to her and the forest, so naturally I end up helping her with various other things."\\
``A forest conservation fund?" Tiffany asked, intrigued.\\
``Oh yes," Raine smiled at her, ``The Glasswoods are a major tourism destination during the festival seasons. The trees themselves attract a lot of industry as well. The forest is a very delicate natural habitat, and the only reason why it is still here with us today is due to generations of Osthryn's family aggressively protecting it over the centuries."\\
``\textit{Centuries}?" Tiffany exclaimed.\\
``Yes, centuries," Raine confirmed, ``Apparently her family has records of being here dating back 1500 years, if you can believe it."\\
``It must be a very large and well-defined family tree," Tiffany observed.\\
``You would think that, wouldn't you? The truth is that some of her ancestry records are missing -- one of the many missions that she keeps herself busy with is trying to piece together family history. It often results in speculative fiction more than fact, but at least it is entertaining to hear at dinner."\\
``She sounds quite the character," Tiffany observed.\\
Raine laughed fondly, ``Oh yes, she is. She is the best old lady I have and will ever know."\\

Valleyton sparked a cozy, lazy atmosphere as Tiffany followed Raine through the town square.
A consistent, low-level hum of casual conversations filtered through the air. 
It was apparently mealtime, since diverse scents of hearty home cooking reached her nostrils when she passed houses and businesses by.
Dogs and children chased one another around the fountain depicting a water-horse in the centre of the square, disturbing the two young ladies seated on the fountain's edge gazing after just-dropped wishing coins.
If Tiffany's sense of style would have been considered vintage or quaint in Grosbergan and Mountainkeep, it would be the height of fashion here.
It was no insult to the women's clothing, whose skirts and blouses bore intricate floral embroidery in bright, primary colours that contrasted well with the otherwise uniformly cream and ocher fabrics.
The garments hung comfortably loose, with minimal structural elements. 
Whalebone corsets were out of place here, instead likely being replaced with the softer and easier to make corded stays.\\

The men, likewise, were relaxed in both their appearance and attire. 
No top hats or waist-coats with high collars and coattails were to be seen here.
Instead, they wore simple ensembles of loose, boxy shirts, some embroidered with similar designs to the womens' attire, and densely woven cotton trousers.
In everything they did, even more so than the denizens of the leisurely Grosbergan streets at Twilight, there was a sense that time would bend to accommodate them.\\

The smooth paving of the town square gave way to the densely foot-traffic packed cobbles of side-streets, which in turn gave way to gravel.
The din of family conversations and the faint sound of stringed instruments lovingly strummed on front porches died away, the sounds and smells of early evening at a lakeside taking precedence.
Tiffany marveled at the quiet. 
Having grown up in the bustling Mountainkeep, she felt Grosbergan was a welcome relief from the frenetic pace of the larger city.
Valleyton, however, completely redefined her expectations of what a small, peaceful settlement was like.
The reverent stillness of the nature immediately surrounding the outskirts of the hamlet deeply impressed on her why this location was such a popular place to get away to.\\

The Scope's domed roof was now barely visible above the tree line. 
The mountain, which had felt like a wall boxing her in while on the train on the way here, loomed large before her.
Looking up at it, barely able to discern its peak, made her feel dizzy and small. 
The scenery of the approaching forest and the pristine lake lazily lapping at its banks managed to soften the feeling to that of being sheltered in a large, ominous hug.\\

The path continued to wind along the edge of the lake, eventually coming up to the foot of a small hill.
Nestled beside it, barely visible through the trees, was a charming, antique stone cottage with a thatch roof.
Light burned warmly through the small windows deep-set in the three-foot thick walls, and the cottage was surrounded with an assortment of haphazardly growing wildflowers.
Hens busily scratched and pecked at the dirt road passing it by, and Tiffany spied a small white rabbit dash from the porch across the road to hide in a bush.
A villager appeared on the steps, stopping to scratch the ears of a well-fed and content black cat perched on the wooden railing who had failed to notice the scampering rabbit.\\

``Good evening to you, Raine!" The villager greeted them enthusiastically as he met them at the base of the porch's steps, a fresh-smelling cheesecloth bag clutched in a bandaged hand.\\
``Good evening! I see Osthryn gave you some rusks for your trouble," Raine returned warmly.\\
``These I bought," the villager dismissed, ``the least I could do. She refused any extra payment, believes that the burn's good healing is naught of her doing!"\\
``Well, I am certainly glad to hear that your burn is healing! Do you know if she still has another patient at the moment?"\\
The villager gestured to the front door, ``Not far as I can tell. I must, however, bid you good-bye. My Lianne is sure to be eager for another batch of Osthryn's aniseed rusks!"\\
And with that, the villager briskly set off.\\

Raine climbed the steps, and passed under the grapevine trellis shading the whole of the modest porch, beckoning Tiffany follow her when she reached the front door.
Tiffany noticed that both the porch and the stonework in this section of the house had to be relatively newer than the rest of the cottage.
Perhaps this was an extension constructed some time after the original building was completed.\\

A small bell announced their presence as they crossed the threshold of the front door into the apothecary.
The sweet musk of potion-making and various salves and poultices hung low in the small room. 
A wick of incense lazily smoked on the long, low countertop, filled with glass instruments and equipment of varying origins.
Tiffany's eyes scanned the shop with intrigue, the equipment ranging from a fairly advanced microscope to a well-worn, antique mortar-and-pestle littering the front counter.
Bundles of dried herbs, bottles of clearly labeled Glasswood tree sap, globs of Glasswood tree resin and several varieties of bark along with other unidentified ingredients filled the shelves lining the wall behind the counter. 
One shelf was dedicated to ready-made potions and remedies, and yet another was filled with empty glass tubes, an impressive collection of various crystals, candles, and bottles.\\

An eccentric beaded curtain covered a doorway behind the counter's barrier to the left of her, likely leading into the main house. 
At the furthermost right corner of the shelves, a wooden door stood closed, leading to some anteroom where Osthryn took her patients.
Piled high in a box well-removed from the potion-and-poultice-making instruments were several cheesecloth bags containing Osthryn's famed aniseed rusks.\\

``Osthryn! I have our lodger!" Raine called.\\
The picture that Tiffany had formed in her mind of what Osthryn would be like was in no way related to what she saw.
Based on Raine's discussions of her and the context clues, Tiffany would have expected a sweet, bent little old lady with arthritic hands curled from age and hard work.\\

The woman that emerged from the anteroom was well advanced in years, but stood far taller and straighter, and had a much more proud and youthful grace to her movements than Tiffany could have imagined.
She was breathtakingly beautiful, the lines defining her face inviting Tiffany into the memories that spawned the expressions that formed them.
A long, thick braid of striking white-grey hair fell heavily to her waist. 
The length of her hair was as notable as her height. 
She stood nearly six feet tall with an impeccable posture that betrayed a refinement akin to royalty.
Her tailored woolen kirtle, while an antique style of garment, likewise stood in stark contrast with the humble cottage surrounded by small livestock.
It was a deep emerald green, matching her expressive and twinkling eyes, and was trimmed with delicately embroidered designs in bronze thread that cascaded down over the bodice to the low-hanging hem.
The cuffs of her sleeves, stopping just below her elbows, were trimmed with matching embroidery.\\

The stately face crinkled into a smile. 
Osthryn moved with decisive speed around the apothecary's countertop.\\
``Oh, how lovely to meet you, Tiffany, dear! Sweet young Helwyn told me such wonderful things about you," Osthryn began, towering over the much smaller Tiffany and firmly gripping her comparatively tiny shoulders in her long, slender and well-conditioned hands. 
Osthryn alternated a brief kiss of greeting on each of Tiffany's cheeks, continuing, ``You must be exhausted from such a long journey. I know for certain from my occasional travels between my home and Grosbergan that remaining seated for close to twelve hours at a time does nothing but evil to your bones!"\\
\textit{Young} Helwyn? Tiffany thought to herself that Osthryn should then very well be close to ninety. 
The regal spell that Osthryn's appearance had cast over the bewildered Tiffany was quickly broken by Osthryn's deeply enthusiastic greeting. 
All the images of a stereotypical grandmother that Raine's descriptions had created clicked comfortably into place.\\

``Oh, it was not too bad. I at least had some good reading to keep me company. Thank you so much for hosting me, \textit{oumee}." Tiffany returned with a bow of her head.\\
Osthryn scoffed good-humouredly, ``At my age we should not have to bother with silly things like honorifics. Call me Osthryn, if you are comfortable to do that. And the pleasure is purely my own, darling," Osthryn placed an arm around Tiffany's shoulder
to guide her through the beaded curtain out of the apothecary, ``an old widow like myself is grateful for the opportunity to have so many different and interesting young people come and go from my home."\\

Raine fondly watched the display, thinking back to her own stay at Osthryn's cottage nearly a decade earlier.
Tiffany was very quiet, but she seemed like she would be a good match for Osthryn's energy. 
That factor often made or broke the stays of the lodgers from the University of Grosbergan.
She followed the two through the beaded curtain to the library, scooting past them with Tiffany's suitcase raised above her head into the kitchen and onto the door leading to Tiffany's bedroom to place her luggage. 
Knowing Osthryn's tendencies to chatter at length with new lodgers, she determined her time was better spent handling at least some of Tiffany's arrival logistics for her.\\

Tiffany looked around in awe at the snug, just left from cluttered library that Osthryn had pulled her into. 
This room was very clearly part of the original cottage. 
The thickness of the plastered stonework wall was emphasised by the foot-and-a-half deep window-sill that was mirrored on the outside.
A small, retrofitted cast-iron stove was pushed into the corner, its smoke-pipe escaping through a hole bored through the cottage wall and bending well clear of the thatch roof.
The cold slate floor was warmly carpeted with an intricately woven red rug, and two comfortable wingback-armchairs sat side by side near the stove, a small footstool in front of one and a short, round table next to the other.
The walls were draped with beautiful tapestries -- scenes ranging from depictions of battle-fields and fantastical scenes of dragons perched on top of castles to intricate and intimate vignettes of fairies seated on the edges of fruit bowls and kelpies splashing playfully in a river.\\

``I gather you enjoy reading," Osthryn began, noting Tiffany's admiration of her tapestry collection with a smile, turning her attention to the heavily laden bookshelves, ``I hope that my collection does not disappoint you. I have worked very hard to acquire it over my lifetime, and after much curation, I feel quite happy with it."\\
The collection was very impressive, with titles ranging from contemporary novels that Tiffany knew well, to thick, imposing translations of ancient spell tomes.
One set of shelves in particular caught her eye -- fully populated with collections of fairy tales, academic treatises on folklore, various histories of nations both near and far, and, most happily, an edition of \textit{Anatomy of Draconic Folklore}.\\

``Oh!" Tiffany brightened, standing on her toes to reach the title, "I was just reading this today!"\\
Osthryn hummed absently, ``A good introduction, I would say, but I find Gravett's handling of the subject a tad dismissive. If you are \textit{really} interested in Dragons, I would recommend this."\\
Osthryn had no need to raise herself up on her toes as she reached for a thin, worn, leatherbound edition just out of Tiffany's reach.
It was nondescript, and simply had the word ``Dragons" embossed into the leather.
Tiffany took it in her hands, running her fingers over the leather binding.\\
``This is a translation of some very early folklore. Don't be fooled by its length, the language is dense enough to take up considerable hours of focused reading. It is, in my opinion, far closer to the heartbeat of history than Gravett could ever claim to be."\\
Tiffany turned the cover to the first page,\\

``\textit{A retellinge of the workes of Oswald the Seeing-Scribe, the first worke writtene in the dayes of King Williame the Wise.}"\\

``Oswald, like the Oswald from S.R. 200?" Tiffany asked, looking up at Osthryn's searching gaze.\\
``That's the one. One of the few of their works to survive the Rationalists' spell-purge of the 500's. This copy is a few decades old. I transcribed it word-for-word from a museum copy, with permission, and bound it myself."\\
Tiffany felt honoured that a perfect stranger who placed so much importance on their books would entrust her with such a precious item.\\
``You are welcome to any of the books in this library that tickle your fancy at any time. I only have two rules, that chair," Osthryn gestured to the armchair closest to the iron stove with the foot-stool, "is mine, and," gesturing to the collection of tomes and other leather-bound works in the lower shelves of the case closest to the kitchen door, ``please ask me before removing or handling any of these much older books. They were difficult to acquire."\\

Tiffany nodded, dumbfounded at the generosity. 
These kinds of books were rare at the University of Grosbergan's library, and she often had to jump through hoops to have precious few hours of access to one, which was often chained to the shelf it came from.\\

The whistling of a tea kettle greeted the pair as they emerged from the library into the kitchen.
Raine was busily laying out teacups and tartlets, well-acquainted with the road-weary appetite Tiffany's arrival at Osthryn's cottage would bring.
Raine's face brightened, and beckoned Tiffany come take a seat at the large Glasswood table in the centre of the warm and welcoming kitchen.
Tiffany ran her hands along the beautiful piece of furniture.
Its top was minimally shaped, the natural curves of the ancient tree's bole preserved in the outline of the solid wood slab.
The table appeared as if it were made from finely sanded dark mahogany wood joined in scattered patches of ocher-toned frosted glass, but it was all one piece.
The wood of the tree itself had grown glassy over time, the original finish being wiped down periodically in sections with an ethanol solution to create the glass-in-wood effect.\\

Tiffany was grateful for Raine's thinking with the tea and tartlets, and was soon comfortably engaging with Raine and Osthryn's easy tea-time conversation.
Her original hesitation regarding the quality of Osthryn's lodging was completely overridden with wonder at her hosts' hospitality and kindness.\\

Raine eventually excused herself to go home and get some paperwork done, satisfied that Tiffany had been properly delivered to her destination.
After greeting Raine, Osthryn led Tiffany to the door of her room.
Without a second thought, Osthryn's fingertips grazed the wick of the oil lamp mounted against above Tiffany's new writing desk, a flame swallowing the wick and bathing the room in a dim glow.
Tiffany took a double take, but concluded that there must be a crystal hidden in the oil bowl.\\

``Here we are," Osthryn gestured to the modest room.\\
It was slightly larger than Tiffany's hostel room, which she was grateful for. 
A properly sized single bed was placed against the far wall. 
The window embedded on the far side shone Sol Priori's gentle twilight light onto the foot of the bed.
The boxes and luggage Tiffany had sent ahead were piled on the bed, and her rolling case was placed in front of the small bedside table that housed another oil lamp.
The extra space allowed for a small, waist-high bookshelf that stood empty at the foot of her bed, and a floor-to-ceiling cabinet stood to the right of her bedroom door.
The extra storage room was welcome, but Tiffany was convinced that her meagre possessions would do little to fill the space.\\

``Let me know if you need any more oil lamps in here, it can get quite dim. This room does not receive a lot of light during the day, but luckily you are just behind the hearth in the kitchen, so you will have no difficulty staying warm." Osthryn spoke, placing a small box on Tiffany's writing desk, ``I will be in my garden if you need me. Tonight I will set out some cold meats and bread for dinner, the weather calls for a light meal. Come and fetch me when you are ready."\\

With that, Osthryn, closed the door, leaving Tiffany to take the day's excitement in. 
Tiffany pulled the writing chair from under her desk and sat down, surveying the room. 
Osthryn was right, it was indeed a bit dim.
Rising, she made her way to the bedside table, and brushed her thumb and forefinger over the wick as she saw Osthryn do, murmuring vague encouragement of light.
No response. 
She did not feel the familiar tension in her skin in response to a stored crystal spell when she tried for the second, and then the third, time.
Defeated, she stood and turned to the door to ask Osthryn what the correct spell-command word she should use to operate the lamp.
She froze when her eyes landed on the small box Osthryn had placed on her desk.\\

Matches. These were ordinary, old-school, unenhanced oil lamps.
Tiffany's exhausted thoughts roiled within her as she struck a match, the second oil lamp bringing a welcome increase in brightness to her small room.
She likely missed Osthryn using a match to light the lamp, there was no way that anyone could activate a spell of any kind without a catalyst.\\

\textit{Yes}, Tiffany thought, kneeling while she unpacked her books one by one into the small bookshelf at the foot of her bed, \textit{sitting for twelve hours on end will do nothing but evil to the mind too.}