% \lettrine{}{} command typesets a drop cap in the document

% second brace set formats text placed inside as small caps
% (same thing as doing \lettrine{L}\textsc{orem ipsum ...}

\chapter{Optics}
\textit{``Dragons' dual identity as both a legend of folklore and a historical beast shall prove to be a consistent confounder in this work. 
For instance, consider the majority of physical descriptions from reliable sources that claim Dragons' scales are coated with a thin film of wax.
Several folklore sources sport reasons for this waxy coating as melodramatic as `...the fingerprints of those devils they have embraced...' (Ildis, S.R. 213) and `...that natural consequence of evil magic, where even one's sweat is thick and unpleasant...' (Astora, S.R. 500); and as standard as `...a marker of inherent, inborn magic, naturally excreted in the course of its use.' (Oswald, S.R. 120)."} \\

\textit{``Whether the waxy coating was evidence of evil intent, devils'-deals, or the result of continued and sustained spellcasting, no level of consistent or academically acceptable interpretation of these claims exist."}\\

\textit{``As archeo-anatomists, we are bound to take the sum of the evidence as provided by folklore, inasmuch as it corresponds to true historical evidence, which excavations and remains readily provide, and then mete out coherent explanations based on commonality.
For instance, this question of wax can very quickly be resolved by combining the folklore claim with a factual observation: Dragons were reptiles."}\\

\textit{``Reptiles, notoriously cold-blooded, often require external means to regulate body temperature.
Dragons, in particular, have the added difficulty of flight. In addition, the cold reaches of the stratosphere are generally off-limits to modern reptiles.
The consensus therefore is that this wax, rather than being some deeply magical side effect, was more likely a reptilian response to environmental demands unique to the Dragons."}\\

\vspace{1mm}
\textbf{As quoted from ``Unearthing the Anatomy of Draconic Folklore" by E. Gravett, first printed S.R. 1056}

\vspace{5mm}
\lettrine{Tiffany}{ hovered over her workbench} with intent concentration, her posture better resembling a freshwater shrimp than a young woman.
The twin suns hung low above the rolling hills outside the laboratory windows; a queue for her fellow students to wind up their work.
Tiffany, precariously kneeling on her high wooden workstool, was deaf to the slowly rising volume of shuffling and chatter.
Her usual pet peeve, the screech of furniture dragged along the well-worn wooden floors, likewise did little to rouse her.
Daylight could wane all it liked, but she allowed the suns no comment on how far her work was from complete.\\

Her workbench was littered with souvenirs of drawn-out failure: crystals, pieces of wire, and discarded rolls of pulse-graph output created a graveyard of trials and errors. 
Likewise, Tiffany herself cut an almost feral quality to her figure.
Her abundant red curls that she had so carefully pulled into submission with a ribbon tied at the base of her neck had begun to escape: falling in ringlets to frame her face.
Her large, deep-set hazel eyes were hollow and lined with shadows.
The dark rings under her eyes conspired with her high cheekbones to lend a more gaunt quality to her pallid face than usual.\\

The laboratory was a moderately large, sufficiently equipped facility.
Alchemists did not need nearly as much variety in components and tools as other disciplines did -- excluding Wizards, who only ever seemed to operate on mood, dusty books and dubious results.
Alchemists' command of simple, repeatable magic allowed them to infuse crystals with various basic spells.
These crystals, when configured in relation to one another correctly, allowed Alchemists to build out more complex and incredibly useful functions.
The crystal itself would affect how the spells infused into it would interact with the world.
Luckily quartz, the most commonly used and reliable crystal variety, was relatively abundant.\\


Tiffany jumped at a sharp \textit{rat-at} on the thick wooden slab that topped the workbench.\\
``Due for an epiphany anytime soon?"\\
Tiffany looked up at the amused Rowan, a researcher nearly ten years her senior. 
Who, in the last two years of her studies, had never given her solid ground from which she could get a good summary of his character.
He was intriguing but slippery: his apparently forthcoming and congenial nature allowed him to deftly side-step any reading beyond arms' length, even with the girls she knew he had slept with.
She took a deep breath to still the startled flutter in her chest.\\
``I could really use one now," she admitted, leaning forward with her palms against the edge of the worktop, her spine thankful for the brief realignment.\\

``All the crystals are already prepared, I made sure two or three different purities of each were available to account for variance in the resistance..."\\
She trailed off, scanning disarray of components in front of her. 
Several sets of crystals had been welded, wicked off, and welded again to the now well-worn support board.
The combination she had now was certainly correct, it lined up best with both her calculations and test expectations -- perhaps it was time to try a different lens?\\

Rowan leaned with a single arm on Tiffany's desk, his free hand on his hip, and looked past her to the setting suns.
Sol Primus was nearly sunk past the horizon, and Sol Priori, the size of a small moon in the sky, still hovered high.
The ticking of the clock that hung above the laboratory's door stretched the silence that Tiffany's mid-sentence rumination failed to notice.
Tiffany's breath hitched when he leaned in over her, her thoughts disrupted. 
His chest was a hands-breadth away from her shoulders, and the flutter in her stomach agreed that she did not know whether this presence looming behind her was welcome or uncomfortable.\\

``Clearly, you have played with the crystals enough, given the state of your board," Rowan commented with a frown, "try another lens."\\
He then pushed himself away from the workbench, pocketwatch chain swaying, straightening his deep blue waistcoat as he stood up.\\
``Thank you." Tiffany politely managed.\\
``When are you packing up? Petr is likely to make is way home in the next few hours."\\
Tiffany gestured to the pulse-graph, ``When that ream of paper is finished."\\

The pulse-graph was a machine with two rollers that pulled a thin slip of graphing paper over a short flat surface, two needle-arms filled with red and blue ink currently hovering over the paper.
The needle arms, with optional attachment for one more, were supported by an intricate set of gears.
Three thin, short stands with a starter gear around an axis mounted through each of them stood neatly in a row, a crystal mounted to the top of each.
Each crystal, when either magic or optic stimulus excited it, would induce the starter gear to turn, causing its attached needle to begin drawing the associated signal.
This needle movement would in turn activate the crystal beneath the drawing surface, activating the gears that spun the rollers that pulled the paper as the signal would progress.\\

The pulse-graph at Tiffany's station had seen plenty of work that day, as evidenced by the scattered slips of rejected signal graphs and the pitifully exhausted ream of paper mounted within it.\\
``Should be safe, depending on how long you take to mount that lens." Rowan commented.\\
He looked down at his pocket watch as Tiffany gave a noncommittal hum in response,\\
``I have somewhere to be, but best of luck to you!"\\
``Thank you Rowan, you must have a lovely evening!" Tiffany called out with a smile when he reached the door.\\

Rowan graced her well wishes with a brief two-finger salute before exiting and continuing down the corridor.
His sure and swinging stride made the brunette waves that hung just past his ears sway in response to each step. 
To Tiffany he painted the picture of a man on a mission, and she silently wondered to herself what it could be as he disappeared beyond the view of the lab's windowed walls.\\
% Action-description of what Tiffany is busy with, with some more emphasis on the magic present in interacting with the items.

Presently she redirected her attention to the project at hand with a sigh.
She resumed her freshwater shrimp posture when she placed her elbows on the table, covering her face with her hands.
Gently she pressed her eyelids with her fingers, the comforting pressure relieving some of her exhausted tension.
Not only was she in the throes of constructing and testing her device, the magic-use itself was proving exhausting.
As an Alchemist, she had to very carefully balance her thoughts and her emotions.
Magic flowed purely through intentions and feelings, and at times too much analytical thought or stress would block the intention of an instrument user, leading to less-than ideal results or simply non-response.
Devices that were available to use by the general public were usually hardened and supplemented with alternative magic generation. 
This ensured these factors had less impact on the devices a non-Alchemist would use, but instruments and tools involved in \textit{creating} devices had to be raw and sensitive to each and every intuitive impulse.\\

With renewed resolve, Tiffany reached for the welding-wand.
The wand had a thick, metal handle that tapered down to the width of a mounted crystal, the words of the embedded spell etched in flowery gilded calligraphy covering it.
A heat-insulated grip on which her thumb and forefinger rested protruded just below the crystal, ending in an extended pen-nib with a small iron-plated copper point.
She drew on her deep desire for a hot drink and a soft chair with a backrest.
Thoughts of a crackling fireplace dying down in a dim, cozily lit library full of flickering candlelight crystallized her intention to heat the wand's tip.\\

Carefully, with a set of tweezers, she gripped the top of the currently attached lens and applied a light upward pressure.
She ran the welding-wand around the lens' base, melting the bonding material that held it steady.
The lens came clean off with little effort, and she placed it to one side to retrieve a length of wicking-braid.
She held the wand on the bonding material to keep it supple when she placed the wicking braid on it, which readily absorbed the now-liquified material, leaving the board a clean surface.
She took a length of the bonding material wire, and, carefully placing it on the board, re-melted a clean line of it where the new lens would be placed.
She selected a new lens, one more concave to intensify the focus, and with her tweezers held it above the now-solidified line.
Softening the bonding material, she pressed the lens into place.
Satisfied that it was appropriately attached and that her linework was clean, she replaced the welding-wand, rapidly cooling the moment she broke contact with it, and placed her little amplifier between a source-crystal and the pulse-graph.\\

Activating the source-crystal, she watched with bated breath as the pulse-graph sprang to life, the crystals in her amplifier rapidly pulsing at varying intervals in response to the source-crystal's signal.
The two needles began to move in tandem, the rollers whirring as they dutifully pulled the paper across.
Silence punctuated by the ever-patient clock and the \textit{scritch-scratch} of the pulse-graph's needles crouched in solidarity with Tiffany's breathless anticipation.
Slowly two lines emerged, and Tiffany hardly felt the hot, joyful tears of relief running down her cheeks as she smiled giddily at what she saw.
The signal was perfectly amplified, whatever having pushed it out of phase before was resolved.\\


\begin{center}
***
\end{center}

With an impossible social grace and an easy come, easy go air, any casual acquaintance would be hard-pressed to believe that Rowan was in any way deeply academically inclined.
Professor Helwyn knew otherwise. 
This easy persona of Rowan's deftly camouflaged the highly driven, professional, and ruthless individual that his former student, now collaborator, had proven to be.
While his social interactions appeared easy and unfiltered, Professor Helwyn had come to know that every move Rowan made was particular and calculated, mimicking the machinations of the mind housed under that \textit{bloody mop of hair}.
It was beyond him that Rowan, at 30, still insistently refused to have it trimmed properly.
Perhaps he truly wished to avoid being taken seriously.\\

A sharp \textit{rat-at} on the doorframe of his office made Professor Helwyn glance up from his work.
A tall, dark, broad-shouldered figure crossed his arms and casually leaned against the doorframe.
Rowan was not overly large, but he easily filled most of the doorway with his presence.
He had materialised as if he were summoned.\\
``I need data," came the demand, serving to complete the announcement of Rowan's sudden appearance.\\ 
Professor Helwyn took his time to adjust his glasses with his middle finger, staring Rowan in the face for a significant beat of silence.\\
``Don't we all?" Helwyn commented dryly, struggling to mask the twitch in the corners of his mouth.
His deeply entrenched smile lines were evidence of a lifetime spent owning a good sense of humour.\\

Rowan gave an exaggerated eye roll as he took a seat in the chair that Professor Helwyn gestured to opposite his desk.
The office was a comfortable size, with dark carpeted floors and an impressively large mahogany desk that was balanced out with a large bay window populated with potted plants on the far side. 
The office was thoroughly lived-in; 
A floor-to-ceiling bookshelf containing decades' worth of textbooks, publications, and students' projects covered the wall to Professor Helwyn's right.
A seldom-cleaned chalkboard decorated with layers of hurriedly scrawled notes and diagrams likewise graced the wall space to his left. 
The imposing desk took up the bulk of the room, and was covered with haphazardly organised piles of documents and notes.
Helwyn's preference for extensive wood paneling would have left the office feeling oppressive were it not for the light emanating from both the generous bay window and the many lamps hanging from a vaulted ceiling.\\

``I have a hunch, and the readings I can make with the equipment here are insufficient. I need something more substantial." Rowan explained.\\
Helwyn began silently rifling through one of several piles of forms on his desk as Rowan spoke.\\
``And what, pray tell, might this hunch be?" Helwyn drawled absently, periodically looking over his glasses at Rowan while he continued his search.
A small ``ah" of victory escaped his lips when he found the form he was looking for, holding it up to the light.\\
``It's... a work in progress. What I do know for certain now is that I need to go to The Scope." Rowan continued, suppressing his irritation at Professor Helwyn's apparent disinterest in the conversation.\\

The last part of that sentence brought Professor Helwin's full attention to him.\\
``You are currently responsible for several projects under you. Data-gathering at The Scope is time consuming, precise work that will keep you away from here for months at a time. Your time is better spent elsewhere. However!" Profession Helwyn lifted his index finger to halt Rowan's immanent retort, ``Have a look at this research proposal," Helwyn continued, sliding the form across the desk, "and tell me that it is \textit{not} in any way related to this hunch of yours."\\
Helwyn crossed his arms as he leaned back in his chair, peering over the rim of his glasses to watch Rowan's eyes flick back and forth while scanning the document.
The silence continued for a few minutes, Rowan going back and forth between two or three of the pages.
Finally, with a sigh, Rowan tossed the form back onto Helwyn's desk, which Helwyn returned to the top of his pile.\\

``It is impressively thorough," Rowan admitted begrudgingly.\\
``Now, if I am not mistaken," Helwyn forged on, ``using Tiffany's readings once her study is complete will kill two birds with one stone, will it not?"\\
Rowan's face coloured with realisation, ``I would like to have access to the readings sooner than that, and you know it."\\
``Now, now," Helwyn smiled, his crow's feet pantomiming genuine feeling, ``You know as well as I that if your hunch is what I believe it is, proper publishing order needs to be established. We cannot have your work be circulated before a project that uses the original data set is complete! It will just muddy the waters in terms of attribution."\\
``You just want your name on there." Rowan deadpanned.\\
``Tell you what," Helwyn offered, adjusting his glasses once again, ``If you find a way to \textit{explicitly} link your hunch to this Tiffany girl's work that creates a real contribution, your name can be on my project."\\
  
Rowan smiled numbly, his eyes barely suppressing the simmering anger he felt. 
Professor Helwyn held Rowan's stony gaze.\\
``So, Tiffany?" Rowan supplied at length.\\
``Have you ever worked with her?" Professor Helwyn queried, absently retrieving a quill and stationery to begin drafting an acceptance letter.\\
``Never directly," Rowan replied, ``but she is precise, if a bit slow," he chuckled ruefully, ``At least I will have high-quality readings if nothing else."\\
Helwyn looked up from his writing, ``Well, I believe that settles it, then?"\\
Rowan stood up, and Professor Helwyn took Rowan's hand outstretched in farewell in a firm shake.\\
``That settles it." Rowan replied with a smile, letting go of Professor Helwyn's hand as he turned to leave.\\
``Oh, one more thing," the Professor held out Tiffany's acceptance letter to Rowan, ``Would you deliver this to my typist to send out tonight? I fear I have kept Tiffany waiting for the outcome of her application for long enough."\\
``Certainly," Rowan bowed his head, before taking the letter and stalking out of the office to the typists' corner.\\

Once out of sight, he brought the letter into his field of view, committing Tiffany's telepost address in the upper right hand corner of the page to memory.

\begin{center}
***
\end{center}

Tiffany's light footfalls on the narrow cobbled streets of Grosbergan matched the lightness of her spirit.
The relief of finally completing her amplifier side-project permeated every step she took.
There was no reason for her to take on that project other than to keep herself busy while waiting for the outcome of her proposal, but, like anything she undertook, she took it seriously.\\

It was already late in the evening, but Sol Priori would ensure that the second twilight would last for several hours, as it had done every spring and summer for the past 150 years.
The buildings that lined the streets she walked in the surrounds of the University of Grosbergan stretched no taller than three stories.
While Grosbergan was a respectably large city, it was still a mostly academic town, and by no means comparable to the other larger cities such as the Capital, Mountainkeep, in either economy or population.
The cobbled streets were broad enough to allow either a single horse-drawn cart or a bustling group of pedestrians at a time, and in Grosbergan, the traffic generally tended toward the latter.
Parks, markets, and places of business were designed to be within walking distance of the population centres they served, and vehicles of all sorts were restricted to areas closest to the sail-train station.
With the exception of the occasional bicycle, wheeled contraptions of all sorts were few and far between.\\

The extended twilight created a relatively new type of night-life culture. For many people in the warmer seasons the day would only begin in earnest once Sol Primus had set. Shops that solely operated during daytime hours in centuries before Sol Priori began to draw close would now open once the work-day had finished. These business hours, the hot-spot of daytime labourers and students eager to utilise the lazy twilight hours for their shopping and leisure, proved incredibly profitable.\\

The streets were quite full tonight, with the laughter of patrons of all ages at the various midnight-cafes and the songs of friends walking arm-in-arm filling the air.
Some folks, like Tiffany, walked with purpose to and from their homes and work, while others merely ambled the streets in search of something to fill their time with.\\

Presently, Tiffany arrived at her hostel. 
It was a tall, narrow, whitewashed building, similar to hundreds of others lining Grosbergan's streets.
Like many of the other buildings, solar sails spun atop the roof, charging whatever instruments the building contained with Sol Primus', and now Sol Priori's, magical energy.
Once she entered her room, she made a beeline for her little cabinet. She immediately began unpacking her amplifier and tools from her satchel into their proper places, as if to make up for the mess she allowed herself to create in the laboratory.
Her hostel room was modest - it boasted a washbasin and mirror, a small writing-desk, a narrow bed and a single, double-door cabinet in which she stored all her possessions.\\

A slow-blinking purple light in the corner of her eye caught her attention. She turned to the telepost sitting on her writing-desk, a clockwork typewriter with a purple crystal mounted on it. 
A collapsible antenna extended from it almost to the ceiling. 
Her breath hitching, she reached out to touch the crystal, and the telepost sprang to life with a clatter and a \textit{ping}.\\

``\textit{Tiffany,}\\
\\
\textit{It is with great pleasure that I confirm your research proposal, `The effects of Sol Priori's seasonal geo-magnetic influence on intention-activated devices', has been approved for funding. In addition, your request for a recommendation to conduct data-collection at The Scope has likewise been approved.}\\

\textit{Your project commencement is within two weeks of this notice's date. Please note that all arrangements for travel to Valleyton are at your own cost. We have a lodging liaison in Valleyton that will provide room and board during your stay at a discounted rate.}\\

\textit{You are welcome at my office at any time within my posted office-hours in the next week to discuss further details regarding funding, deadlines, and expectations.}\\

\textit{Kind regards, and congratulations,}\\

\textit{Professor Helwyn.}"\\

Tiffany sat down hard on the edge of her bed. 
She could hardly believe her luck.
She had an idea that she might have enough funds for the journey and the first month or two in Valleyton, if she would be able to find employment there.
She looked at her cabinet, luckily she did not have much that needed to be packed...\\

Tiffany shook her head, she needed to take this in.
Her project was approved. 
She had a recommendation to use The Scope. 
She was going to see The Glasswoods and the Glasswood trees, a living legend.\\

She looked back down to the letter in her hands, a tremor betraying her excitement.\\

\textit{Oh, what a sail-train journey this will be.}