\chapter{Bark and Bite}

\begin{center}
    \textit{The anger stoked in a gentle man's soul is rarely quenched. \\
    Woe be to him who sparks the flame.}\\
\end{center}

- \textbf{A saying of King William the Wise} \\


\lettrine{Raine}{had determined that the best cure for stiff joints} and a weary mind after a long day of travel was a brisk, energetic hike early the next day.
The sparrows had barely begun their song to announce the beckoning rays of Sol Primus before Raine arrived in a flurry of enthusiasm at the cottage. 
She had little difficulty rousing the bleary-eyed Tiffany, the latter complaining bitterly to Osthryn's great amusement.
A serving of aniseed rusks chased by a stiffly brewed cup of tea and a quick retrofit and approval of Tiffany's outfit later, the two young ladies set out on their expedition.\\

The morning air presently corrected any lingering grogginess in Tiffany, who had warmed up enough to the land of the living to enjoy Raine's running commentary on her morning so far.
Raine suggested that she and Tiffany take their hike up to the Scope. 
That way, she could see one of the routes she could take when she would begin walking to it in the mornings. 
Tiffany readily agreed to the idea, her excitement at the prospect of seeing The Scope in person two days earlier than expected washing away any resentment of the distance.
At the foot of the mountain path that lead directly up to the Scope, Tiffany and Raine ran into a potential third member of their party.
Henry did not need much convincing to join them, needing to do his rounds in the forest anyway, and was keen to meet Osthryn's latest lodger.\\

And so the three set off on their trek. 
Tiffany fell silent and retreated comfortably into her shell while she listened to the two close friends' easy back and forth.
While Tiffany was used to walking everywhere in Grosbergan, she fatigued unexpectedly quickly once they had made some progress up the mountain trail. 
The elevation above sea level in combination with the trail's grade and difficulty fell well outside the realm of what she was used to.
The long journey of the day before, coupled with a less than ideal night's rest in an unfamiliar location, likewise conspired against her.\\

Raine maintained her speed easily, ever the mountain goat, and was eager to tackle the climb.
This allowed Tiffany and Henry a turn to speak to each other when he opted to walk behind her, Raine long since overtaking them and leaving them behind.
Tiffany was grateful for the ranger's slow and patient company, and the thoughtfulness of his gesture to intentionally slow down when he was more than capable of outpacing Raine was not lost on her.
Henry made no mention of her ragged breathing, and when he felt it necessary, naturally slowed the procession down by stopping to point out some interesting flora or fauna.\\

``There is an easier trail through the forest," Henry reassured Tiffany when she sat down on a rock to catch her breath, feeling quite pathetic when faced with the prospect of likely making this climb every day.
Tiffany smiled at him weakly, too focused on slowing her heartbeat to form a proper reply.\\
``Raine!" Henry called after his friend, the latter still determinedly pushing forward several yards further up the mountain.\\
Raine stopped and cupped her hands, ``I have the keys! I will unlock so long!" she called down in response, before turning and resuming her bounding climb up the trail.\\
Henry chuckled and rolled his eyes when he sat down next to Tiffany on the rock, pinning his shortbow into the ground between his legs and leaning on it like a walking stick.\\

``She started you off too quickly," Henry told Tiffany sympathetically after a short, comfortable silence, ``Raine has been stuck filling out paperwork, sitting in stuffy offices negotiating with the barristers, and dealing with one too many uncomfortable interactions with stupid people for the past few weeks. I think you were just the excuse she needed to go running up the mountain like a lunatic," Henry explained, his golden-green eyes appearing washed out in the bright morning light as he looked to the horizon the three had left behind them.\\
Tiffany, still catching her breath, followed his gaze.\\
``It's ... beautiful," She managed.\\
It certainly was beautiful.
The early morning was still cool, and the hamlet was slowly stirring to life.
Wisps of smoke rose lazily the chimneys where families were starting their breakfast.
The lake, as usual, was pristine as a pane of glass, the only ripples present were trailing groups of ducks and the occasional rowboat.
Henry leaned over and tapped her shoulder, bidding her to follow his hand when he pointed out the path that ran from the cottage, along the lakeshore, before disappearing into the trees.\\

``That is the path people usually take from Osthryn's to The Scope. Raine and I walk it often too. It is mostly a tourist trail: well-marked and has a longer serpentine pattern on a lower-grade slope. The only real climb is the last few yards where that trail merges with this one at the end," Henry looked down at Tiffany, her face pale with nausea and flushed with exertion cementing his plan for the return journey, ``I reckon we should take that path back down, I need to double-check some things in that area anyway."\\

``Sounds like ... a good idea," Tiffany replied haltingly. 
Henry gently laughed at the evident exertion it took her to speak.\\
``You don't need to impress me with your conversational skills. Take a second and enjoy the view. Breathe in deep through your nose ..." Henry instructed, demonstrating an exaggerated breath in through his nose that he held for two seconds before exhaling through his mouth.
Tiffany followed suit, feeling her fluttering heartbeat slowly normalise after a few deep breaths.\\
Henry satisfied that she was looking less in danger of imminently falling over, stood up and held out a hand to her.\\
``Ready to go?" He asked.\\
Tiffany nodded, taking the offered hand to pull herself up.\\

The two set off again at a reasonable pace. 
Henry still paused every few paces to have Tiffany join him in admiring a wildflower, or once, a lizard that stood atop a rock with its chest proudly puffed out, seemingly to challenge the hikers to an honour-duel.
Presently, and thankfully without further incident, Henry and Tiffany joined a satisfied Raine who had perched at the foot of the stairs inside The Scope.\\

The Scope was even grander than the view from the train could ever have suggested.
The domed roof had Tiffany feel like she had crossed the threshold of a cathedral when she entered it.
The staggering array of equipment, sensors, and communication devices shrunk away in the presence of the one instrument that necessitated the domed roof's construction.
In the centre of dome structure stood the Scope's namesake.
A great telescope, larger and more imposing than any she had ever seen, stood surrounded by a spiral staircase cordoned off with a locked gate at the base of the stairs.
The main lens was probably large enough for the three of them to stand on each other's shoulders and still not span fully span its diameter.
The eyepiece was not attached to the telescope itself, rather it sat at one of the equipment stations, facing down at a glass slide.
A matching crystal on the side of the eyepiece matched a second just like it that sat at the end of a long array of reflecting mirrors and various lenses leading from the main scope.
Tiffany assumed that the images captured through the Scope's lenses were somehow transmitted the short distance to the eyepiece hovering over the glass slide.\\

A tap on her shoulder brought Tiffany's attention back to her companions, Raine holding a set of keys to her.
Tiffany took them, reverence evident in her slightly trembling fingers thankfully ignored or unnoticed.
``Here are the keys to the front door, the dome section controller, and the majority of the equipment stations. Letitia, who is a primary maintainer here, will show you how everything works and which keys are to be used for what. The only keys you don't have," Raine added significantly, ``are the keys that let you through the gate onto the stairs. Those are available on special request only, and with supervision from Letitia or another senior maintainer, to prevent death by neck-breaking and tampering with the Scope itself," Raine explained.\\

Tiffany nodded, looking from the keys in her hand around the building once more.
A thought occurred to her, ``Why isn't Letitia handing these keys over?"\\
Raine smiled and pointed to a small equipment station in a darkened corner that was well removed from the Scope's eyepiece, ``See that? That's my station. I am just a botanist, ..."\\
``... \textit{just a botanist}," Henry interrupted with a scoff.\\
``...but most of my low-light experiments I did back in the day I did, and still do, here. I spend a lot more of my time working on conservation now, but I am a maintainer here. Just not as senior as Letitia," Raine continued with a glare in Henry's direction, ``I also owed Letitia a favour. The main reason, I admit, is that I really needed an excuse to go on a hike today."\\

Henry laughed out loud, ``See Tiffany? Told you this was all a selfish plan."\\
``Oh, come on, don't think I did not notice how you enjoyed spending some time with our guest, Henry," Raine countered knowingly with a twitch at the corner of her mouth.\\
``I was an afterthought in this scheme of yours, Raine, if it were not for me, poor Tiffany would have expired on the mountainside!" came the retort.\\
``She was \textit{fine}, nothing like a little heart rate spike to welcome you to The Glasswoods!" Raine continued with an unabashed grin on her face, winking at Tiffany.\\
``You did start her out too fast, Raine," Henry stated, his voice serious.\\
Raine's demeanor deflated somewhat at that, ``Sorry Tiffany, I do sometimes forget to pace for others while hiking. It was especially difficult to slow down today. I hope it was not a terrible shock to your system.\\

``To be honest, I was embarrassed at how much I struggled, given that I always walk so much while at home," Tiffany admitted, ``But I do think that city streets and mountain trails aren't that comparable," she offered with a smile.\\
Raine, happy that her stunt did not completely offend their newest arrival to The Glasswoods, gave Tiffany a grateful squeeze on the shoulder.\\
``I think that we should take the easy way down, what do you think, Henry?"\\
Henry nodded his approval, ``I suggested it to her earlier. I need to check on our tapping hot spot that the trail passes any way."\\
``Then that settles it!" Raine declared, setting off from the Scope at a decidedly more measured pace.
Raine and Henry paused for Tiffany to lock the doors behind her, drinking in one more look at the Scope before turning and joining them.

Henry and Raine's banter soon started up again as the three made their way down the mountain, background noise to Tiffany while she took in the scenery of the valley below her before it disappeared behind dense forest.

\begin{center}
    ***
\end{center}

The slower descent under the cover of tall conifers was already a better experience for Tiffany, who had by now forgotten the morning's mountainside ordeal.
Raine and Henry had fallen companionably silent as they eventually did on all their walks through the forest, and Tiffany was quietly drinking in every sight and sound.
The orb-weaver spiders made impressive displays in the branches overhead, the fast-disappearing dew droplets thankfully still visible enough to grace the intricate webs with an effect like they were dipped in diamonds.
The crunch of forest-floor debris and gravel beneath their feet was an oddly immersive sound to Tiffany, who eventually came out of her shell enough to feel comfortable hopping from debris to debris after the satisfying \textit{crunch} with childlike wonder.\\

``So, Tiffany, I am merely a \textit{humble ranger}, and my \textit{fine assistant} here is just a botanist," Henry began, teasing Raine with a poke in the ribs, who hissed at him in return, ``but I am interested to know, what do you need the Scope for?"\\
Tiffany stopped dead with her feet firmly pressed together as she landed with a \textit{crunch} on her final heap of pine needles, looking up sheepishly at Henry and Raine who were watching her expectantly.\\
Straightening herself and trotting to catch up with them, she asked ``What exactly do you want to know, the type of readings I will be taking, or why?"\\
``Let's start with why," Raine suggested, ``Osthryn mentioned a few aspects of your research proposal, and I saw some of the back and forth with Helwyn, but I would like to hear it in your own words."\\
``Why's a good enough place to start as any," Henry agreed, swinging his shortbow back and forth in his right hand absently.\\

Tiffany continued walking, her hands pensively folded behind her back while she stared at the tops of the trees around her, thinking of what to say.\\
``So, you know how we say that our power, the power of all living creatures, comes from the sun?" She began.\\
``Not like how you probably mean it," Raine responded.\\
``Well, probably almost exactly like how I mean it. Plants can't grow unless they have sunlight. Animals can't survive without plants to eat, and without the sun's heat we would be a frozen rock in space. But on a deeper level, magic itself is powered by the sun."\\
``That I think we all know," Henry supplied.\\
``Yes, but, to get specific, we all have an inherent \textit{animal magnetism}. To a greater extent, some crystals and other elements, when imbued with a spell, can be \textit{induced} by our inherent magnetism to enact those spells that we enchanted them with. We cannot create the \textit{effects} of these spells ourselves, but for some reason, if there is a catalyst like a quartz crystal imbued with the spell present, previously inert spells can actually have an impact on the world around us."\\
``So, what does this have to do with the sun?" Henry probed.\\

Tiffany continued, ``The sun, particularly Sol Primus, has its own magnetism. In a twelve-year cycle, Sol Primus has hot-spots of activity that wax and wane, called sunspots. These sunspots are theorised to shoot hot masses of magnetised material at our planet, which, with its own magnetism, repels the incoming material. This interaction, however, charges the general magnetism available in the air, influencing our magnetism and the magnetism of all living beings. This is also where Solar Sails gather their power. The magnetism present in the air when these masses collide spin the Solar Sails, charging whatever devices these sails are tethered to. This allows folks that are not trained magic users to use the devices that we have imbued with spell magic without inducing the spells themselves.
Sometimes, like with Sail Trains, the sails are used to amplify the Alchemist's own induction to greater effect.\\
To make a long story short, over the past 150 years, Sol Priori has grown closer and closer to our planet. Sol Priori, just like our own sun, Sol Primus, has its own cycle of hot-spots. It follows that the introduction of even more ambient magnetism in our world over time will change magic, probably unpredictably."\\

``So what are you trying to measure? How much magnetism Sol Priori is introducing into our system?" Raine asked.\\
``I am hoping, that by measuring the amount of sunspots visible on Sol Priori over the next six months, hopefully longer than that, along with the ambient and acute magnetism present, I can project how an ejection from Sol Priori will influence our magic over time."\\
``One important question," Henry interjected, ``If Sol Priori has been close enough to give us a second \textit{day} for the past 150 years, why hasn't magic already started acting up?"\\

``That's the cool thing!" Tiffany exclaimed excitedly, ``Stars also spin on their own axes. Sol Primus spins a bit faster than Sol Priori does, and we orbit it, so we are likely to regularly intercept an ejection in our direct system. That has kept our magic going since the dawn of time. Sol Priori, on the other hand, which only passes close enough for direct observation roughly every 2000 years, spins very slowly. To put it simply, we don't know if and how it will influence magic while it is here. I have a strong feeling based on other research that I have read that we might be close to a point in Sol Priori's spin where we will be faced with a very active set of sunspots in the next year or two, but by then it will be too late to protect ourselves."\\

Henry instinctively reached out to steady Tiffany who had begun balancing precariously on a fallen branch during her wordy explanation, ``Protect ourselves from what?" he asked.\\
``... hmmm?"\\
``Protect ourselves from \textit{what}?" Henry pressed.\\
Tiffany blinked and shook her head, her large hazel eyes coming into focus.\\
``Well, the outsized surge in magnetism," she answered, hopping off the branch and coming to a standstill, Henry reactively swung his other arm to catch her, letting it fall to his side when he saw it was unnecessary.\\
``It will likely disturb or destroy all magical understanding as we know it."\\

``I doubt that massive assumption was anywhere in your proposal," Raine interrupted dryly, having fallen increasingly silent, irritated at the nonchalance with which Tiffany made such large claims.\\
``No. I wouldn't put something like \textit{that} in there. That is just speculation on my end, but it is the core of my \textit{why}. I want to at least have a start to figuring out what will happen and when," Tiffany admitted, ``my proposal is limited to measuring what hot-spot activity from Sol Priori I can, and trying to correlate some effect that activity would have on a small selection of instruments."\\

``Hmm," Raine hummed noncomittally, thinking it best to let the subject change itself.\\
Speculations and claims of this nature tended to put her on edge, and Raine knew that her temper would not last long in this line of conversation.\\

``Oh. No." Henry breathed.\\
Raine did not need to wait long for a swing in the conversation to present itself as Henry took off to the side of the trail. 
Beckoning Tiffany to follow suit, Raine followed him, freezing in her tracks when she saw the source of Henry's sudden despair.
A Glasswood tree, that must have been growing healthily for at least the last 200 years, stood with a six-foot high section of its trunk fully debarked all the way around.
Raine felt woozy. 
This was destruction and abuse of the highest degree.\\

``I am so sorry that the first Glasswood tree you get to see in person is like this," Raine told Tiffany mournfully.
She watched Henry desperately circle the tree, looking for any evidence of who could have desecrated the stately giant in this way.
Tiffany stared at the scene with a mixture of wonder and grief.
The Glasswood tree was almost personified in how its branches grew and reached for the sky. 
The thick, knotted bole told the story of the tree's long history, its diameter at its largest point stretching sixteen feet or more.
The bark was coarse and dark, like an oak, and its leaves were broad-bladed and plentiful.
The stark, six-foot wide stripe of viciously stripped bark marring it sullenly declared that this sight was not to stay.\\

``Any hope we can save it?" Henry asked Raine, storming back to the trail, his gentle demeanor undercut with a savage combination of desperation and rage.\\
Raine shook her head, ``I don't think we can. The bark was stripped off too deeply, and the ring is too broad. The tree would have dried out beyond the point of no return within hours."\\
``But... but we can try!" She added in response to Henry's desperate expression and her own despairing hope, ``There is no chance that we would pull it off, but at the very least we can try to wrap it and hope for the best. It is the least we could do."\\

Henry stood motionless with his hands in his hair for several tense moments, eventually closing his eyes with a deep sigh, muttering, ``By Dragons' blood. Those bloody poachers."\\
``I am not going to the barrister's office this time, not with this. Especially not after what Arnwi said to me," Raine pleaded, her realisation of what must have happened sinking like a stone to the pit of her stomach.\\
``Don't worry about that," Henry placed a reassuring hand on Raine's shoulder with a firm squeeze, "I will take care of it."\\
Raine gave Henry a look, ``How are you planning to do that?" she asked with apprehension in her voice.\\
``Properly," Henry replied with a half-smile, some of his usual gentle demeanor resurfacing to reassure Raine, ``Don't worry."\\

``Let's get a move on," Henry said, stepping forward at a brisk stride, ``The longer we let this tree just stand here, the more likely it dies. And Tiffany," Henry continued, looking at her with genuine sorrow, ``I am deeply sorry that the poachers stole your first Glasswood from you."

\begin{center}
    ***
\end{center}

The Kelpie's Bridle was one of two pubs in Valleyton, and of the two, it was more bar than pub.\\
Where patrons of Duckbill Inn would happily bring their young children to run and play between tables while ma and pa shared a good lazy, greasy meal and a pint or two, The Kelpie's Bridle was decidedly more exclusive to men who could grow beards and women who could choose to marry.
This, and that Valleyton was a village where all the residents had to do in terms of leisure was fish, hike, or have a drink, often in that order, Henry had a firm idea of where to find Arnwi.\\

The Twilight had long since ended by the time Henry made his way to the Kelpie's Bridle. 
The lake, ever still, reflected a perfect image of the night's constellations.
He and Raine, with Tiffany and Osthryn's help, had desperately tried to wrap the wounded tree with mismatched lengths of cobbled-together cloth coated with as much wax as Osthryn could muster.
It would not be enough, and Henry knew in his bones that it was a lost cause. 
The thought of losing one of the most ancient and prolific Glaswood trees to senseless and, honestly, \textit{clumsy and incompetent} poaching, wounded him deeply.\\

The faint strumming of a kitar accompanied by rhythmic thrumming on a hand drum greeted Henry when he entered The Kelpie's Bridle. 
The late hour and, more likely, the characteristic odour of wisdomroot smoke rendered the background music slightly off-tempo and the patrons thinned out and dazed.
Most of the chairs were already placed upside down on their tables, sending the message that the barkeep wished to head home soon.
What dancing there was earlier in the evening hours was now over, a single man pathetically shuffling ironically off-rhythm to the already off-tempo music.
He shook his head in reassurance at the exasperated barkeep, who, satisfied that Henry would not be ordering anything, resumed passive-aggressively cleaning out glasses and mugs.\\

Henry pulled a barstool closer, choosing to ignore the characteristic tacky feeling of spilt liquor under his fingers, and seated himself next to the severely inebriated Arnwi.\\
``What a day, eh, \textit{boss}?" Henry started, his voice low and dripping with acidic sarcasm, ``Six by sixteen foot of Glasswood bark is nothing to sneeze at for an honest day's work."\\
His comment had the desired effect.\\
``Wass it to \textit{you}? Take it to my barrissther, he should set you ...right ...sthrait." Arnwi spat, the slur in his words betraying how far his profits of the day brought him in terms of liquor and, Henry scrunched his nose, wisdomroot.\\
Henry smiled, the waft of the ironically named smoker's vice cementing his plan in his mind. 
Henry stole a glance at the barkeep, who was keeping one eye on the situation, some of the earlier passive-aggressiveness washing away in favour of curiosity.\\

``Oh, I know it was you," Henry continued, looking down while he fidgeted with a large splinter coming up from the bar, ``only you would do such a \textit{terrible} hack-job of it."\\
Arnwi lurched forward, his face inches from Henry's, the foul breath triggering every impulse Henry had to gag -- but he kept his face as neutral as he could.
``You have no evidencsse..." Arnwi reminded Henry, shoving a finger way too close to Henry's eye, ``Talk...t'me ... barristher."\\
``Oh there is plenty of evidence, Arnwi," Henry went on, pushing Arnwi's hand out of his face.
The wisdomroot had lent an unnatural bloodshot quality to Arnwi's eyes, and his pupils were so wide they filled whatever space his irises would have occupied.
Henry strongly suspected some poppy-crystal was in the mix too.
Arnwi was celebrating \textit{big} tonight.\\
``The layers of bark were so haphazardly cut, the gouges left in the tree so crooked, deep, and ragged. Only the most \textit{incompetent} of poachers would do \textit{that}," Henry taunted, ensuring he raised his voice just enough so that he was clearly overheard by both the nosy barkeep and the dubiously sober patrons.\\

``I am a good poacher! The best there is, I got that bark from right under your nose you blood-drinking, dog-teat-sucking ranger!" Arnwi exploded.\\
The whole bar stood silent at the outburst.
Arnwi, oblivious to the implications of his public admission, gripped the side of the bar to balance himself.\\
Henry remained seated, stone-faced as he held his ground.
Arnwi, high on his wounded pride, fatally continued, ``Your chattering \textit{bitch} ain't much of an \textit{ranger} either, and I bet I could get to \textit{her} right under your nose too."\\
``Like how you tried to threaten her, you insidious little \textit{wyrm}?"\\

Arnwi staggered back into his stool, clumsily swirled his bottle, and lifted his drink to his lips, ``I wouldn't listen to the tall tales that bitch has ... to tell" Arnwi drawled conspiratorially.\\

Blackness crept into the edges of Henry's vision as he leaped to his feet and grabbed hold of a fistful of Arnwi's hair, bringing the smirking devil's forehead down hard on the side of the bar.
``Unfortunately for you," Henry growled, his voice dangerously close to the edge of madness as he forcefully lifted the groaning Arnwi close to his face, still gripping his hair, ``I hang on to every word that \textit{bitch} breathes. If you ever, and I mean ever, lay your hands on Raine, or step foot in that forest again, I will make sure you live to regret every second of it."\\

``Talk.. to my barrister," Arnwi mumbled, clearly too little happening upstairs to comprehend the fullness of the situation that he was in.\\
Deeply disgusted, Henry let go of Arnwi's hair and let him fall back against the bar.\\
He ignored the silent, gaping stares as he stalked out of the bar into the night air. The crisp spring freshness in contrast to the heavy wisdomroot-stink he emerged from did little to bring him from the deep, boiling rage in his chest.
Doggedly he dismissed the thoughts from his better self that he had done the wrong thing, that he had put the case in jeopardy. 
Arnwi had crossed a line.
The tree was one thing, but Raine?\\

Raine he would kill for.

\begin{center}
    ***
\end{center}

Arnwi staggered drunkenly through the streets of Valleyton, aimlessly searching out either revenge or sleep.
The Kelpie's Bridle closed shortly following Henry's confrontation, and the barkeep satisfied that Arnwi had no concussion and was thoroughly capable of taking a hike to hopefully walk off a cliff face, rushed the man out.
A sharp, stinging wind whipped the reeds when he neared the lake, alerting Arnwi that he had stumbled in the opposite direction that he had intended to go.
Still high, and seeing double, he looked into the lake's surface, his bruised forehead developing an impressive shiner.
Arnwi laughed at his reflection.\\

Another cold wind whipped through the reeds, this time whirling in a tight circle around him.
Arnwi, frightened, staggered back from the water's surface.\\

``Sins, sins! You see, I have seen yourrs!" cried a man's voice in an exaggerated, lilting northern accent.\\
Arnwi turned, his heart beating in his throat.
Standing before him was a translucent image of an old man, tall and wastingly thin.
A long, sharp chin and bushy eyebrows were distinctive features of the spirit's wrinkled face.\\
His attire was odd, anachronistic.
His trousers were cut off above his knees, and a button-down plaid shirt with the sleeves similarly chopped below the elbows was tucked into it.
In his hands, he held a large, generously smoking pipe, from which the ghost took a good, long draw.\\

Arnwi began to giggle uncontrollably at the sight, and the ghost humoured him with a good belly-laugh of his own.\\
``Ghosts...ghosts don't smoke!" \\
``Such a generralisation!" The ghost returned in kind, his mirthful smile fading as quickly as it came, the silver glow that emanated from him darkening to a threatening hue.\\
The exaggerated accent disappeared, ``Men don't gut and steal my trees. Men don't hurt young ladies."\\
Arnwi stumbled over his words, unsure if he was imagining his conscience, or if he truly were facing a vengeful spirit.\\

``The Governor sends her regards."\\

With that the ghost disappeared in a swirl of smoke, reappearing as his face twisted and contorted, growing longer and more pointed.
The old man's eyes glowed with power, and smoke poured from his eyes and nostrils.
Silver horns slowly formed on the sides of the contorted visage, a shimmer akin to scales filtering as a mirage through the spirit's haze.\\

Arnwi grabbed at his own throat, desparately gasping for air.\\

Words would have escaped him were he able to retell the last thing he saw before he drowned.