\chapter{``Oumee, Oumee"}

\begin{center}
By the Dragons' blood, guard your eyes \\
Lest you be tempted to an early demise \\

By the Dragons' blood, watch the skies \\
Lest you be caught in your lies \\

By the Dragons' blood, treasure your ties \\
Lest you be the bane of all that is wise \\
\end{center}

- \textbf{Dragons' Eyes, a popular nursery rhyme, circa S.R. 812}\\

\lettrine{The days}{passed quietly} enough for Tiffany once she had settled into the rhythms of her life in Valleyton.
The Scope, while it remained impressive, soon became as familiar and mundane to her as it was to her fellow Scope residents. Raine visited her little experimentation corner more frequently now. The case against the poachers had reached a stalling point when Arnwi went missing. Tiffany had little context for the circumstances of his disappearance, but Raine was not forthcoming with any information. Tiffany decided that the best thing for her and Raine's fledgling friendship was to avoid the subject. Raine was treating her somewhat cooler after Tiffany's revelation of her personal magic theory to begin with, and Tiffany was unsure what or who caused this subtle shift in attitude. She certainly did not want to aggravate it by participating in gossip about a subject that clearly bothered Raine.\\

``Do you know tales of kelpies, Tiffany? They are fae-creatures, wiley and unpredictable. They appear near large bodies of water, often in the shape of a man. When the victim of the tale approaches them, they transform into a water-horse, drowning the unfortunate soul. If you are lucky, and you manage to put a silver bridle over their heads, you can capture them and have a very industrious fae-horse! You know, Raine, perhaps that Arnwi was last seen leaving the Kelpie's Bridle is no coincidence -- perhaps he met his fate at the hands of a kelpie in the lake!"\\

Letitia, on the other hand, found great amusement in pressing Raine for details in the dull waiting times between observations.
Tiffany bit her tongue, watching Raine from the corner of her eye while she adjusted the eye-piece of the Scope for the next observation cycle. Raine scarcely looked up from her seedlings, but Tiffany noticed her jaw muscles tightening in irritation.\\

``A Ghillie Dubh might have lured him into the forest and had him fall through a trapper's hole of his own making into the fae-wild for all I care," Raine returned, not skipping a beat in her work.\\
``A Ghillie Dubh, now that is an interesting creature, Tiffany. They are benevolent fae that fell out of favour with the fae-queen, so they are stuck on this side of the veil. For their love of Petra, they roam dense forests protecting plants, animals, and children. They are gentle souls -- much like Henry. Henry would make a good Ghillie Dubh."\\
``And you would make a good sin offering to Prof. Helwyn if you keep distracting Tiffany with folklore while she is working," Raine tersely warned.\\

Letitia chuckled, ``It is like clockwork. If you begin to sound like you are admiring Henry, Raine shuts you down. It is astounding, Raine, that after nearly a half-decade of working so closely with each other you and Henry are not yet an item."\\
Raine had made her way over to where Tiffany was making her observations and Letitia was supposed to be instructing her on the instruments. Raine smiled, ``I only shut you down when you are being silly, Letitia. Henry would not possibly make a good Ghillie Dubh, he cannot grow a proper beard!"\\

Tiffany breathed a sigh of relief when the two dissolved into laughter, the issue seemingly dropped. She never could be quite sure when someone was teasing or serious, and it was a puzzle she often found too exhausting to tease out. Raine turned her attention to Tiffany, her social discomfort not escaping her notice, ``It can get boring up here sometimes, Letitia loves pushing buttons when she can."\\

``Speaking of pushing buttons!" Letitia interjected, recovering from her own laughter, ``Let's see if we can finally get the sun-sail meter and this little amplifier of yours synchronised."


% The technical details of the scope are discussed further with a scene of Tiffany setting up some of her equipment

% They walk back down to town together, and Tiffany ventures to ask Raine about how the case is going. They run into Henry in the forest, who is being very quiet and withdrawn the last while.

% Tiffany arrives back at the cottage with Raine, and Osthryn is ready with a newly baked apple pie with some strange ingredients. 
\begin{center}
    ***
\end{center}

``Oumee Osthryn!"\\
The greeting rang out in tandem with the apothecary's doorbell to signal the entrance of the day's first visitor.
Osthryn patiently looked up from her work, the use of ``Oumee" characteristically signaling an acquaintance she wished to keep at arms' length.
Arnwi's barrister came practically bounding into the apothecary, his face painted in false concern. 
Osthryn matched the expression with satisfactory curiosity.\\
``How can I help you today, Barrister Michel?" She smiled patiently.\\
The barrister was practically bursting out of his skin, ``I have some unfortunate news regarding your case, Oumee," Barrister Michel began, wringing his hands, ``Is there any chance that you have a private moment to discuss it?"\\

Osthryn walked around the counter and latched the apothecary door, flipping the sign hanging in the windowed door to ``Closed."\\
``Certainly. Come with me to my kitchen, discussions like this always warrant a cup of tea."\\
Barrister Michel followed her into the kitchen, openly gawking at the statement Glasswood table in the centre of the room.
Osthryn patiently put the kettle, still warm from this morning's brew, on the stove.
The silence did not need to stretch long before the kettle whistled its characteristic screech, and Osthryn, adding two sets of leaves into the separate cups, poured slowly.\\

``Jasmine, my favourite," she said, pointing to the tea-leaf jar she had conspicuously added her own leaves from, "not really a crowd-pleaser, if I am honest. You take Oolong?" she said, setting Barrister Michel's tea down before him like there was not a question that he would drink it.
Barrister Michel took a sip with an ingratiating smile.\\

``So," Osthryn began, watching as the Barrister set the cup down on the table with a wince at the temperature. 
Osthryn closed her eyes briefly and tapped on her teacup with her fingernail, ``What is the problem?"\\

``Oumee Osthryn, it is truly tragic news. Arnwi was found early this morning, drowned in the lake!"\\
Osthryn raised her eyebrows, ``Truly, that is disturbing news. What could have befallen him?"\\
Barrister Michel's tone darkened, looking at Osthryn with a hint of malicious victory, he said, ``Your ranger, Henry."\\
``Surely Henry did not \textit{drown} a man. What do you have to place him?"\\

