\chapter{Road Rash}
\begin{center}
\textit{In our youth, where the streets are alive\\ our words run over with idle lines\\ In our youth, when we scaled the singing tree \\ we longed for what would come to be \\ In our youth, in our dreams we retold \\ futures, desires, and denial we'd be old \\ Oh, in our youth, \\ In our youth}
\end{center}
% They go and report back to Auntie Osthryn, and decide it is a wonderful plan to stay for dinner, an idea she, as usual, 100% gets behind.
\lettrine{An}{exasperated hiss and splutter} escaped Henry's lips, the ranger desperately swiping at his face. 
He sharply directed his attention with indignant alarm at the culprit.
The small, struggling spider quickly righted itself back onto its feet and harmlessly skittered around the branch out of sight.
Satisfied that the offending creature had truly left him in peace, Henry settled back down into a squat, bow balanced over his knees as he wiped the last of the sticky cobweb remnants off his face.\\

Carefully, he leaned his weight onto the bole of the tree, his right leg stretched out the length of the branch, his left coiled like a spring beneath him.
From his perch, if anyone stalking that area would have been able to see him through the thick foliage in his lincoln green shirt and dark trousers, he appeared in all senses as a dancer.
His height was moderately above average, tall enough for others to take note of it, but not so tall that it was a defining characteristic. 
What was more notable than his height was his \textit{length}, his slender limbs taught with firm, compact musculature that gracefully flowed with the long lines of his frame, any bulk purely attributable to his bone structure.
His hair was trimmed short, with the effect that the cow's lick positioned right at his forehead caused his fringe to remain straight up in the air with no additional hair to weigh it down, no matter how much wax he used to try and tame it.\\

Henry shifted his weight fully onto his left leg and nocked an arrow, eager forefingers resting on the bowstring in anticipation of the draw.
Raine said that the poachers had begun encroaching on this area, and without a positive identity, there was nothing they nor Osthryn could \textit{officially} do to prevent the unsanctioned felling of Glasswood trees.
Raine's idea was to spook them by shooting the trees they scoped as they walked by them. 
Once sufficient arrows were loosed, Raine would emerge from her hiding place, they would give chase, and hopefully, they could identify the offenders so that Osthryn could bring a legitimate accusation. 
This harebrained idea would serve two purposes she claimed: one, the poachers would likely be thoroughly spooked, and wait a while before moving in on another part of the forest, and two, the bark damage from the arrows Henry would shoot at the trees would stimulate resin production, saving her the effort of tapping the trees herself.\\

The Glasswoods were at first appearance an ordinary forest of biodiverse evergreen trees, a temperate valley woodland surrounding the aptly named Glasswoods Lake.
It housed all manner of wildlife, a beautifully balanced ecosystem carefully managed by Osthryn in her spare time in association with biologists like Raine and rangers like Henry. 
In recent years, the modest budget and demanding lifestyle whittled their crew down to mostly Raine and Henry as full-time caretakers.\\

A shuffling in the underbrush was his queue to draw the bow taught, green eyes narrowing as he fixated on his potential target, practiced, sinewy muscles effortlessly keeping his arms still despite the high draw force.
As much as he truly enjoyed his life in Valleyton, these poachers were beginning to prove a nuisance he could not be too glad to soon be rid of.
The namesake of the Glasswoods, the Glasswood tree, is a valuable and rare species, attracting interest from both eager tradesmen and dogged poachers alike.
Most of the time Glasswood is used as a statement material for beautiful, intricately crafted pieces of furniture and smaller articles, famously used to great effect as wine and whiskey barrels.
The beauty of Glasswood, and the origin of its name, is that continued exposure to alcohols eventually causes the wood to become translucent -- the effect playing off like a warm frosted glass.
Beside the vanity use cases the wood provides for, its resin, bark, and sap comprise important components in both traditional and mainstream medicine.\\

It was clear to most why these slow-growing, climate-finicky trees were such a delicious poaching target.
Henry just wished it were clearer to those with the money to really protect them.\\

An arrow loosed materialised his feelings, the shaft quivering as the arrow embedded itself centimeters away from the emerging head of a poacher rising from his crawl through the undergrowth.\\

\textit{Shit. That was close.}\\

Henry's breath hitched, the close call freezing his hands and feet in a wave of dire cognizance.
Shaking his head, he reached back for a second arrow, nocking it to take aim for a second shot, the calming rhythm of his breath returning as he took aim at the second unfortunate soul rising up from his own crawlspace two trees down.
The first poacher had stood frozen in the immediate aftermath of his reckoning with near-death, barely able to yell a warning to his companion before the arrow embedded itself deep in the bark of the second tree, taking some of the second poacher's eyebrow hairs with it.\\

\textit{Too close. Again.}\\

Henry was surprised at how clearly his malevolent feelings were betrayed by his bowmanship.
He did not have much time to dwell on this realisation. 
The thicket below him erupted into a cacophony of shrill screams with Raine emerging larger-than-life in a drapery of loose shrubbery and twigs loosely tied to a net fashioned into some sort of suit, charging with a scream that would wake the dead while wielding a club overhead.
The rattled poachers matched her with their own shrill cries as they turned to run.
With an eye roll at the display, he loosed a final arrow that cemented the poacher's decision to flee, the fuzzy, club-swinging monster screeching behind them.\\

His position sprang into action, shifting his centre of gravity back into a squat, he sprang straight up into the air.
Letting himself fall past his branch he grabbed with both hands on the branch below, hanging on for a second to break his descent before he dropped feet-first to the ground.\\

The shorter man managed to sidestep Henry's swipe at his waist, prompting Henry to immediately to transfer that momentum with the flat of his hand to the taller man's Adam's apple.
Henry's fingers closed around the man's neck as the blow stalled him, allowing Henry to grab the back of the mask and lift it off his opponent's head. Dark eyes and a familiar high-bridged nose stared back at him.\\

``Arnwi?!"\\

An elbow came down hard on the bend of his arm, his grip loosening just enough for Arnwi to land a haymaker on Henry's temple.
Henry staggered backward, and Arnwi resumed his flight to catch up with his companion, deftly stepping on and around rocks and bushes in the emerging forest path.
Henry looked up just in time to see Arnwi push Raine mid-sprint to the ground, interrupting her chase of his companion, before resuming his flight.
Henry's legs pumped up and down with his arms in perfect locomotion, taking Raine raising herself from the ground in the corner of his eye as reason enough to stretch for the chase in good conscience.
The rapid footfalls of Raine behind him permitted him to push himself faster, vaulting over the fallen Oak in his path, fondly known as the Smoking Log, his feet splashing in the shallow stream running past it, barely noticing the water that fell into his shoes.\\

Henry was lanky and strong, but his muscular endurance favoured short bursts of energy and longer, sustained runs at a lower pace than this mad dash.
The figures of Arnwi and his shorter partner began to disappear through the trees, the building lactic acid in his body and the quieting footfalls of Raine seeming further and further behind him made his decision.
Henry slowed to a stop, turning to look at Raine who had slowed to a trot behind him.\\

``You okay?" Henry asked, studying his companion.\\
Her hands were on her hips as she shifted from one foot to the other to catch her breath, club and bush-suit long abandoned where she had briefly kissed the ground.
Some scratches were visible on her forearms that broke her fall on the gravel and undergrowth, the sleeves of her loose blouse rolled up to just above her elbows.
The fabric of the woolen split-skirt she wore was agitated at the knees, the frayed fibres caked with dirt. Her dark brown hair, usually worn loose, was tightly braided, some flyaways sticking to the sweat of her olive-toned face.\\

``Yeah..." Raine looked up at him briefly, her brown-green eyes meeting his own in curt reassurance.\\
She began dusting herself off, wincing as her raw palms brushed against the coarsely woven wool of her garment,
``Just some road rash, which is to be expected. Did you get a look at your guy?" She queried, straightening herself up again.\\

Henry looked at the cloth buff crumpled in his hands before glancing back in the direction their unwelcome guests escaped to, ``Arnwi, I think."\\
Raine winced imperceptibly when she crossed her arms, cocking her head as her eyes flicked between Henry's prize and the copse of trees the culprits disappeared into.\\
``One of them is local, at least. That gives us something of a lead." She offered hopefully.\\
Henry slowly pocketed the buff, setting off at a measured stride back to the thicket. Raine skipped into step with him, her cadence slightly heightened to keep up with the taller ranger.
Raine scooped up her creation and her makeshift club as they neared their destination, silently allowing Henry to mull over his perceived failure in this exercise.\\

Raine made a beeline to the arrow sites when Henry stopped at his abandoned lookout tree to retrieve his bow and quiver.
Touching the bark surrounding the ingress point, she smiled in satisfaction. The arrow had pierced the bark and embedded just far enough into the bole to create the start of a tap-line.\\
She happily bounded to the second tree to further evaluate Henry's work, stopping in her tracks when her toes clipped against an abandoned satchel, clearly dropped in the chaos she gleefully caused earlier.\\

Her jaw fell open at the contents -- a flask of alcohol, dye, a tapping spout and a mallet. 
Hurriedly she turned the satchel about - searching for any identifiers that would mark its owner. 
Arnwi was young, and she counted on him making a stupid mistake.
Nothing jumped out at her, but the satchel itself was well-crafted and somewhat personalised.
She hoped that the craftmanship and intricate burnt-in leaves at the edges of the closing flap would make this satchel identifiable enough, coupled with Henry's identification of its possible owner.\\

What was most valuable to her and their case was the equipment.
No hiker would be carrying a tapping sprout and mallet, and no harmless visitor would have \textit{dye} in addition to a plausibly deniable flask of alcohol in their pack. 
This was a poacher looking to find, mark, and target Glasswood trees.
Raine brightened as she shoved her find into Henry's hands, who had come up behind her.\\

``Look! More than a name. Must have dropped it. All the hallmarks of illegitimate intent too, no hobby-tapper or hiker would include dye in their kit. This was a red-handed scoping expedition, and we stopped it!"\\
Henry had to relent and share Raine's joy at their unfolding success. 
With the buff, the name, and the pack, they would at least be able to create enough trouble for Arnwi that he would know he was watched, and they would have a shot at a mostly peaceful spring for a change.\\
``Now come!" Raine insisted as she made her way to her hiding spot to retrieve her tools, ``This day is already far from a waste. Let's leverage our head start and have some actual work done!".\\

Henry glanced again at the arrow embedded in the tree, the sap lazily dripping down from the shaft.
A lone droplet of dark orange Glasswood sap shone eerily red in its reflection of the light filtering through the forest canopy.
Henry stood entranced, watching the droplet grow and stretch in response to gravity, the red hue dissipating as gravity finally pulled it from the shaft to land on his shoe.\\

``Here, pull the arrow, keep it straight so that it does not open the tap line larger than is needed. Don't want to cause an infection."\\
Looking up from his shoe, Henry took hold of the shaft with both hands. 
Bracing on his heels and tensing his upper back, he removed the shaft with a brief, sharp tug.
He stepped back, arrow in hand, as Raine perked up with her tap spout and mallet, gently tapping the spout into the opening and busily preparing a catchment for the readily trickling sap.
Watching her work for a beat, he set off to the other tree, ready to repeat the process.
He wondered at Raine's silence at his aim -- perhaps in her own excitement of the day she did not notice how close Henry had come to being a murderer.
She may also just be ignoring the subject.
In either eventuality, he was grateful.
This was not something that he wished to process verbally.\\

With both trees tapped, and all evidence and belongings gathered, the two set off back through the Glasswoods.
Raine, satisfied with the day's outcome, silently fell into step with her abnormally quiet companion.
The burning of the road-rash on her forearms and palms had abated in the course of her tapwork, but was beginning to flare up again when the trees began to thin out and the wind, no longer kept at bay by thick tree trunks, began to whip at the sleeves of her blouse.
While she physically paled in comparison to the ranger striding beside her, Raine herself was no slouch when it came to activity.
The young botanist was well used to, and thoroughly enjoyed, long walks between her home in Valleyton, the Glasswoods, and Osthryn's lakeside cottage, and her work in the forest frequently required her to vault, clamber, leap, and balance far more than any other purely academic position would have.\\

Raine started her stay in the Glasswoods as many that come from Grosbergan do, as a visiting University of Grosbergan student lodging with Osthryn at her cottage.
Her lodging with the eccentric apothecary was a convenient placement - the cottage's proximity to the forest gave her prime access to collect samples for her work, and Osthryn allowed her to use the apothecary's supplies and workspace after-hours to conduct her experiments.
With this access, Raine was able to use her time in Valleyton far more effectively than many other fellow students who came here for their botany practicals did.
She soon fell deeply in love with the Glasswood tree itself - a fascinating species that just kept on giving questions in tandem with the answers she found.
Once back in Grosbergan, she quickly found that her heart was lost on more than the Glasswood tree.\\

The moment she finished her post-graduate requirement, she opted to return to Valleyton to make a living there. 
The quiet town, with bursts of tourist activity, high general safety, and friendly locals suited her just as much as the ample hiking trails in the region did.
The main draw for her upon her arrival was once again the Glasswood tree. 
This time with the intricate ecosystems populating the forest that housed it and the lake it bordered.
Osthryn was the estate-holder of much of the land that the forest covered, her family having settled in the region for generations. 
She ran a fund for foresters, both seasonal volunteers and full-time workers.
Raine had no trouble finding full-time employment there, happily embracing the luck that her love and interest in the region's species as well as her newfound passion for working outside had perfectly coalesced.\\

She looked with a fond smile to her companion, the colleagues themselves were not half bad either.\\

Presently the pair of friends found themselves free of trees surrounding them, coming upon the shore of the vast Glasswoods lake.
As usual, they paused to admire the reflection of the setting suns on the lake's pristine surface, reeds swaying with the wind, water lazily lapping the shore, a family of ducks making a desperate stretch to swim the length of the lake by some unknown deadline.
Dragonflies and frogs lazily conversed in the shallows. 
A small white fox with sattelite-dish ears tiptoed to the water's edge, skittering away once it had a drink.\\

The scene altogether respected for what it was, they turned to follow the path along the shoreline. 
A copse of trees rose into view as they climbed the hill to signal that they had come near to their destination.
The stone cottage was modest, but cozy, just large enough to house two to three people comfortably without complaint.
The thatched roof hung low over the thick, ancient stone walls.
No light shone through the windows from their perspective, but the thin wisps of smoke rising from the sturdy chimney in the centre of the cottage's length accompanied with the faint smell of stewing pottage told the companions that the kitchen was indeed still in business.\\

Making their way around the darkened extension, they came around to the back door, which invitingly stood open at the end of a small footpath winding through rows of raised garden beds bearing both herbs and vegetables interspersed with various species of hardy flowers.
Two small windows with deep-set sills on either side of the back door bore flower boxes containing both cooking herbs and toxic plant species that were thankfully cultivated separately.
A warm glow filtered through the intricate lace curtains into the small and densely packed garden, a tall figure seen passing by.
Through the doorway the kitchen beckoned, gently illuminated with flickering oil lamps and the orange glow of the wood stove.
The aroma of venison slow-cooked with cloves and bay leaves bloomed ever stronger when they reached the threshold.
Raine and Henry carefully dusted off their feet before treading on the hallowed cooking ground.\\

``Hello Osthryn!" Henry called brightly when he entered, he and Raine dropping their burdens to the floor in the little alcove next to the entrance. 
Raine hurriedly placed her makeshift foliage-suit outside when she realised how much dirt she was likely to drag in with it.\\

``Oh, hello darlings! What a lovely surprise!"\\
Osthryn came into the kitchen from the library where she had replaced a recipe book, a broad grin matching her outstretched arms in enthusiastic welcome.
Every time Raine and Henry came to visit she greeted them with a genuine sense of surprise and joy -- however, the consistently generous portions she cooked betrayed her expectation of every occasion.
Long, white-grey hair fell over shoulder to her waist in a loosely constructed plait, tied with coarse packing string in a crude but decorative bow.
Her emerald-green eyes twinkled with warmth, the crows' feet around them as deeply entrenched as the frown lines on her forehead.
She was a woman who was unafraid of thinking and feeling, and the story of her life was etched onto her skin for the world to see.\\

Her precise age was a mystery to those around her, but that it was a great one was no doubt. 
She had been the ``old lady" of the village for as long as Henry could remember, and while her visible age progressed slowly over time, she never seemed to deteriorate.
She stood straight and unbent, immaculate posture supported by a well-fitted set of stays, her natural height making her just shorter than him by half a hand.
She single-handedly managed her garden and affairs with ruthless efficiency - running her apothecary with only occasional help in addition to providing basic wound and health care services.
If her time was not already fully consumed by being a highly popular de-facto folk healer, she managed to establish herself as Valleyton's premier provider of rusks of various varieties, which she happily sold to her patients; an eager captive audience.\\

Henry was certain that this boundless energy perpetuated itself: the more she did, the more she kept herself young doing it, which meant, in turn, the more she could do.\\

``Come come, take a seat. You both look exhausted!" Osthryn fussed, gliding over to the wood-burning stove to check on the pot's contents, a new, sharper note mingling with the aroma filling the room shortly after.
Henry and Raine happily obliged, their long day in the forest leaving them quite hungry and grateful for the respite.
As usual, Osthryn refused help with setting the table, moving just quickly enough that if Raine had stood up to help her Osthryn would be done before she could be any help at all.\\

``What happened here?" Osthryn sharply demanded, reaching for Raine's forearm. Raine winced in response to the bony hand snatching her arm up in a decisive grip.\\ 
``Road rash, we were chasing some poachers today," Raine explained, Osthryn hovering her fingers over the scratch marks.\\
``We will take a look at this properly after dinner,"\\
Osthryn released her arm, and Raine gratefully returned her hand to her lap.\\
``Anything useful come out of it?" Osthryn directed at Henry.\\
Henry pulled the buff from his pocket, handing it over to Osthryn, who took it readily. 
``One of the men had this over his face. I am sure it was Arnwi that I recognised."\\
Raine took a bite of her stew, noting most of the heat came from something more than just the dish's temperature.\\
Osthryn absently looked between Henry and the cloth buff she held, standing up from her dinner to pluck a single hair from Henry's head.\\
``Ow!"\\
``Just to compare..." Osthryn cooed as she disappeared through the library, eyes intent on the buff in her hands.\\

Raine giggled into her spoon at Henry's astounded expression.\\
``Well don't look at \textit{me} like that."\\
``...Why did she need my hair?" Henry laughed, the corners of his mouth twitching with both confusion and amusement.\\
Raine shrugged, going for another bite, ``Who knows why Osthryn needs anything?"\\
Henry returned her shrug, ``Fair enough," a bite into his stew resulting in a cough and a hand over his mouth, ``what did she put in here?"\\
``Capsaicin." Raine dryly supplied, adding at Henry's eye roll, ``Peppers."\\
Henry looked down at his bowl as if it would bite him, and gingerly tried a second bite.
Raine wordlessly passed him a jar of sour cream that was set on the table, of which he gratefully added a spoonful to his stew.\\
``Where would Osthryn get peppers like this? Aren't they incredibly expensive?" Henry puffed, red-faced, the cooling effect of the sour cream evidently not as strong as he would like.\\

``Not if you cultivate them yourself!" Osthryn cut in with mirth, returning to her spot at the dinner table with a small bottle of watery red liquid that she promptly added generously to her portion.\\
Raine could not hold her laughter at Henry's pained expression at the display -- his thoughts oscillating between the value of the peppers and the pain he would be in if he dared touch Osthryn's bowl.\\
``You would not have seen it yet, but I have constructed a new hot tunnel in my garden. 
It is quite small, but the seedlings that that you brought back from your last trip to Grosbergan took very well to it, Raine!" Osthryn gestured proudly to the preserve jars tightly packed next to one another in rows above the kitchen cabinet. 
Two jars, clearly recently sealed, sat packed to the brim with red peppers.\\
``The peppers grow incredibly quickly in the correct conditions. I was able to harvest from two plants just this spring already!"\\

``Now," Osthryn continued, giving each Henry and Raine a pointed look, ``tell me more about today. Where on earth did your road rash come from, Raine?".\\   
The table erupted in easy dinnertime discussion, Henry and Raine alternating between, and correcting, each other's perspectives of the day's events.
Unnoticed by either Raine or Henry, Osthryn's eyes darkened dangerously at the mention of Arnwi pushing Raine to the ground, an event that was quickly laughed off by the pair as an occupational hazard of looking after the forest.\\

After the meal was finished to Osthryn's satisfaction of the pair's appetites, and Raine's road rash appropriately seen to, a round of cards was played accompanied by strongly brewed tea.
As usual, Osthryn did not allow the two friends to depart unless they were well-laden with samples of the day's baking exploits.
With a final thanks to the pair for their efforts, and a lecture to Raine on adequate road-rash care, Osthryn set them off on their walk back to their homes in Valleyton.
The articles they had retrieved from the chase they left in her care, along with Raine's bush-suit that Osthryn declared would make fine compost.\\

Sol Priori had begun to finally sink over the horizon when they neared Valleyton proper, the true night's sky glittering with stars.
Raine studied her friend next to her as he walked her to her smallholding.
The close calls earlier that day had not escaped her notice, nor his dampened demeanor following it. 
Henry was not the type to voice his concerns openly, but neither was he particularly good at hiding them.
She hoped he knew that the fluke in his aim this morning was merely a mistake, and not the symptom of anything deeper.
