\chapter{Crystal}

\lettrine{Tiffany} narrowed her eyes skeptically at the crystal. 
Her long, slender fingers twirled it around and around in the light.
No imperfections were revealed in either the magelight or candlelight.
None that should have this outsized impact on her circuit anyway. 
The sunslight would be no use.

The false day was still young when the last fellow student left the laboratory, but now it was truly twilight.
A small part of Tiffany dismissively insulted the beautiful stretching golden and pink hues that accompanied the setting of Sol Priori. 
Even the twin suns themselves can have no say in when she decides to finish her work.\\

Especially if they would decide to be useless to her task in doing so.\\

Sunslight would usually have been her final, desperate bid with which to find any crystal imperfections. 
Unfortunately, she could not progress to that check this time.\\

Perhaps Sol Priori could have a say in when she would be finished.\\

Or, perhaps, she could stop hyper-focusing on this particular crystal and just pick up another one instead.\\

Tiffany looked across her workbench at the seemingly infinitely stretching [Name] Laboratory.
It was not truly infinite.
It was just a long room.
The several rows of identically spaced workbenches across the length of it did make it appear \textit{longer} than it truly was, however.\\

Or would the workbenches make it appear shorter? They should, technically, especially since they were placed nearly from wall to wall in the width of the laboratory.\\

Tiffany sighed at the sight of the crystal dispensers mounted along the wall to her left.
Dizzying quantities of quartz were haphazardly sorted into baskets by some system of size, grading, colour... imperfection rating...\\

Her attention returned to the crystal she was turning over in her fingers.
Any progress made, no matter how false or misdirected, would be lost the moment she chose another.
Those categories were guesses at best -- and pure lies mostly. 
Tiffany has no idea \textit{how} the imperfection ratings were truly arrived at, since the deviation from reality was so strong. 
They were practically useless as a design consideration.\\

Perhaps it was her alone that was always blessed with an incorrect imperfection rating.
No other student at the School of Alchemy of the University of Grosberg had such \textit{luck} as she.\\

The magelight flickered to life as the magelamps slowly lit themselves in tandem with the final retreating rays of Sol Priori.\\

``Oh.''\\

Tiffany could have kicked herself.\\

The crystal imperfections were not the problem. 
The rating was correct.

A very clear band of white through the rose of the quartz crystal told her all she needed to know.\\

If she had thought to turn on the main magelights of the laboratory in the lab earlier, before Sol Priori began to set, Tiffany would have known that this crystal was the incorrect colour.\\

``Sorry, Sol Priori, it was not your fault after all.'' Tiffany breathed as a defeated sigh guided her hands to cover her face.\\

The magelights were not to blame either, she was yet to apologise to them too.
What could have posessed her to miss this stripe? 
Everything inside her convinced her that this was the correct crystal to choose.\\

Why...

``Wait,'' she mused to herself as she glanced over at her design, crystal still turning over in her fingers.\\

``It \textit{is} the right one... I need the white band... why...''\\

Tiffany halted when her eyes fell on the amplifier lying in pieces in front of her. 
The [catalyst item] lay just barely connected from the center mount. 
When did \textit{that} come about? Tiffany was so sure, almost convinced, that the [catalyst item] was connected correctly.
That would certainly make the spell fail, but it could not have been the problem that started this whole mess. 
She was absolutely sure that it was connected when the problems started. But...\\

Carefully, she set down the crystal and picked up a pair of tweezers. 
Gingerly, she picked up the [catalyst item] and held it against the amplifier's [mount thing] as she prepared the soldering wand in her other hand.\\

It was a fight for her concentration to get the wand going.
At this hour, Tiffany was overdue for a break: a nap, a walk, something to drink.
Anything.
But she had nothing to do except wait at this point in the Semester, and she needed to do \textit{something} to keep the madness of waiting at bay.
She had to finish this.
Even if the urgency was wholly self-imposed.\\

Fire. Heat. Fire. No, wait, too hot. We are sitting by a hearth, not burning a forest down.\\

``Like a hearth. Like a hearth.''\\
Tiffany repeated under her breath, closing her eyes for a moment as she allowed the emotions that the scene of a hearth with a dog at her feet to evoke her intention for the wand.
The wand responded to her prompting.
Sputteringly, at first, like her concentration. 
Her eyes flew open, and she studied the crystalline glass as its colour stabilised with its temperature.
A little while longer and she felt confident enough to place it gently against the [catalyst item], soldering it firmly to the [mount thing].\\

She allowed the wand to subside in its heat as she pulled it away from the [soldering point].
Her eyes narrowed again as she set the tools down on the workbench next to the amplifier.
What could have gone wrong?
Why did not refuse to pick anything up that she tried to run through it?\\

Tiffany straightened up on her precarious perch, her shoulders protesting the prolonged [pronation/bendedness].
These laboratory workstools were not designed for comfort.
Not that Tiffany would have minded it.
The only thing she could blame for the relative discomfort of the wooden stool digging sharply into her shins was her poor choice of seating posture.\\

She pulled the design closer again, and began poring over it thoroughly.
Nothing, besides the misjoined [catalyst item], appeared out of place.
The crystal was scrutinised again.
Like Tiffany had determined before, it was the right colour category, and she really needed to concede that the impurity rating was correct by this point.
Perhaps the size?\\

Her eyes narrowed again.\\

``Size... size... size...''\\

Wincing against the pins and needles, she lighted onto the floor and made her way to the weighscales on the other end of her bench. 
``Her'' bench. Ha.
No student really had an assigned bench, but everyone had a ``spot".
Especially if they, like Tiffany, decided that spending far too many hours past [first twilight] in the [Lab Name] lab was a preferable way to pass the time while waiting for the verdict on a life-changing application.\\

At this point, she could have claimed squatter's rights for this bench with how much time she has spent here the last several weeks.\\

The crystal clinked onto the weighscales, the [magical 7-segment display that must still be invented] flickering to life in response to the crystal's presence.\\

``Too light. Just a smidgeon too light...'' Tiffany muttered as she picked up the crystal from the scale. 
Force of habit, or perhaps intuition, stopped her before she made it all the way to the crystal dispensers to fetch a new one.\\

Turning on her heels, she marched back to the weighscales, and picked up a [technical term for the adjustable measurement thingy]. 
She measured the [four cardinal planes], and each fell into the expected range for the size class of the crystal she needed.\\

``Then, why are you so light? Are the impurities off after all?''\\

Tiffany held the crystal between her fingers to the light again, squinting.
This could not be right.
She was back to checking for impurities again.\\

Something else must be amiss.\\

Then the exhaustion hit her all at once.\\

Tiffany fought against the despair of her rest-starved mind.
There was not much thought behind her marathon stint in the laboratory -- not much more than a desire to keep her thoughts practically occupied above all else.\\

She could have chosen a pleasanter occupation for this end.\\

Pleasanter occupations were less effective at warding against the abject boredom and frustration of waiting.\\

Nonetheless, Tiffany found herself with her head sunk into her crossed arms over the workbench, the crystal sitting teasingly before her barely open eyes.\\

Right size.
No impurities.
Too light.\\

``Oh...'' Tiffany groaned in defeat.
What a fundamental mistake.
No matter how a saner incarnation of herself would have gone to sleep ages ago and avoided this unnecessarily drawn-out encounter with her own [mistake-prone synonym].
This was something of [classic, collossal, hilarious] bent.\\

Taking the crystal into her hand again, Tiffany straightened and pulled the notebook kept under the scattered sketches and designs. 
Luckily, this spell component was well-accessed, and the notebook practically fell open at the correct page.\\

[In a fantasy magic language based on old gothic maybe commences a spell.] 
\textit{"Harmony, harmony. You create such harmony. No voice of your own, but you bring others together, resounding in unison -- this concludes the spell 
[some more rhyming and fanciness required here. Basically describing some sort of band-pass filter or a component of it. Also - refresh your memory on how amplifiers are 
supposed to work.]"}

[Description of emotional intentions here too. We want to emphasize how Tiffany relies on her emotions to get a spell to work.
She thinks it is the letter of the spell, like how it works with other spellcasters, that makes the spells work for her. 
She thinks the emotions are just some sort of crutch, like a mnemonic for studying.
She does not realise that they are the primary mechanism by which SHE casts her magic.
We need to find ways to describe how she experiences casting her magic and then contrast it with the reality of how other spellcasters experience it all while staying within 
her point of view.]

Tiffany hardly needed to look at the crystal in her hand to know that the spell was finally taking.
The slight weight that an imbued spell inexplicably added to any catalyst, especially crystals, made itself known in her palm.
Just to be sure, she went to the weigh-scales again to check the crystal's mass.\\

There it was.
The correct weight -- well within the tolerance of what was required by the amplifier's circuit.\\

"Any earth-shattering revelations tonight, Epiphany?"\\

The [soothing, lilting, between-baritone-and-tenor], easy tease from Rowan fell in step with her relieved sigh at the reading on the [magical seven segment display].
Tiffany squeezed her eyes shut for a second before turning to face him, a tired and rueful smile painting her face.
If she only knew how she appeared in this state.
The only colour left in her was the shock of her abundant red curls, and even they had to compete with the dark circles under her eyes.
She hardly took notice of such things when she felt the need to keep busy like this -- but Rowan's arrival put some of her foolishness into perspective.\\

``Nothing that would qualify as an epiphany, unfortunately.''\\

Tiffany did not choose the nickname.
She hardly knows whether it is a sarcastic jab or a compliment that she had it.
Rowan was almost the only one who used it, and it was usually when she managed to accomplish something royally stupid.
Though, sometimes, he used it expressly when she accomplished something royally \textit{not} stupid. 
A wiser young woman than she would have chalked the nickname up to its rhyme with ``Tiffany''.
Tiffany was too clever to give much heed to wisdom, and she knew that it was not just a rhyme.
Especially not when Rowan used it in situations like this.

``Oh, well certainly only a true stroke of genius would warrant you staying in the [Lab Name] for all hours,'' Rowan smiled [wolfishly but less cringe adjective].
He crossed his arms as he leaned against the door to the lab, shifting his weight to his right leg.
The picture of [being in total control and being totally amused at what he is seeing.]
``Any particular reason you find yourself among these deserted workbenches, scrounging away at your scratchings and sketches while you let precious energy burn at the mercy of the magelight?''\\

``None truly. How about yourself, Rowan?'' Tiffany tried to muster as casually as possible. 
She picked up the [welding wand] and prepared to heat it again, cursing the nervous shake of her hand under her breath.
Tiffany was not what one would call a shy girl. 
She kept to herself, enjoyed quiet company, and preferred dancing to herself unseen when she was not reciting [spell-formula components] or working on her artificing. 
But she was not shy.
She was certainly not a nervous person in general when it came to social interactions. 
[Find a way to show this, not tell. 
This is a really cringe and really long infodump about this character. 
I know this is a 'vomit draft', but come on Chara. This kinda stinks!]
[Madman, Architect, Carpenter, Judge. 
This is Madman phase. 
Just put words on the page.]\\

But when it came to scrutinising her work, and especially with Rowan, her social fortitude seemed to fail her.
It did not help that Rowan, a handsome and rakish [fantasy-equivalent postdoc] seven years her senior, was, well... handsome and rakish.
The fact that he took to making up dubiously complimentary nicknames for her (nickname, just Epiphany so far, but it stuck) added to the confusion of her social [skills, fortitude. There is a word I am looking for and cannot think of here.]\\

And she had just done something stupid.
And he did just call her Epiphany.
Which he does when she does something stupid.
So now she was tired, had just realised a good portion of her tiredness came from a really silly mistake she made, and Rowan was here to see it.\\

Tiffany could forgive herself for her hands shaking slightly as she held the wand between her fingers and the [social skills on manual mode feeling] as she attempted to keep conversation with the new arrival in her workspace.\\

Not really her workspace, but, as was the case, people had their spots.\\

``Oh, I had some letters to write and thinking to do. I am hoping to get some time to go to the Scope this year. Don't think my chances are that high though.'' 
Rowan sighed as he pushed himself off the doorframe. 
He ambled over to where Tiffany was trying to [join/solder - fantasy word or normal word here?] the final piece of the amplifier to the [mount].
``It seems like Professor Helwyn has more important things for me to keep my time occupied with."\\

The [welding wand] touched against the crystal gently perched with tweezers upon the [mount].
Tiffany struggled to let her mind focus on both the sensation of heating the wand to the correct intensity while citing the incantation with Rowan's conversation perching on the stool next to hers.
She let herself appear rude for a moment as the final join took hold.\\

``Wha-why's that?" she finally asked once she replaced the [welding wand].\\

A small [rumbling chuckle or scoff. Don't know what fits this character better] escaped Rowan's lips, ``My time is more valuable at his personal disposal than doing what I wish with it, Epiphany darling.''
[condescending poplap vibes but Tiffany still has a crush on this asshole even if she picks it up subconsciously.]

Tiffany kept her hands busy preparing her test and her eyes from his face as a small flush of embarrassment glanced across her cheeks. 
"I meant to ask, what are those things that are more important?" Tiffany measured out slowly.\\

``Whatever His Majesty the Professor wishes.'' Rowan [theatrically Astarion'ed sarcastically - find ways to express this thing I am hearing in my head when he says this.]
Tiffany allowed a small laugh to escape her at Rowan's exaggerated tone. 
He continued.
