\chapter{Surface}

\lettrine{Tiffany} stared out over the surface of the lake. 
Shining in the moonslight like a dark, perfect mirror. 
The stillness was a contrast to her -- one that usually would have served to calm what roiled inside under any other circumstances.\\

Circumstances, what a word for what was done here. 
A \textit{happening?}. 
More accurate, but still too weak.

Catastrophe would be too strong a word, and yet it still lacked the handle to evoke the devastation of her own active part in it.\\

Devastation is wrong too.\\

Wrong.\\

That's it.\\

It's all wrong.\\

But what if it isn't?
What if the face reflected in the dark, mocking mirror surface of the lake was telling the truth?
The dirt streaks that obfuscated her freckles and the tendrils of hair that stuck to her temples were witnesses to the truth.
Tiffany refused it.\\

Even if the moons that dance beside her face in the lake's surface witnessed it all, even if the darkness held the truth of who she was,\\

it is still\\

\textit{Wrong}.\\

She put a hesitant step forward, the toe of her leather boot disturbing the cold surface of the water.\\
Tiffany gave a half-smile at the rippled distortion of the image.\\
Her boot edged further down into the cold, Tiffany watching idly as the water slowly bathed the many buttons that fastened her boot in the icy cold one by one.\\

Solid ground met her foot, a sluggish cloud of silt marring Tiffany's view of the buttons.\\

Ten buttons.\\

She had counted ten buttons covered when she put her foot down.\\

``Its late and cold, Tiffany. Come away.''\\

Tiffany took her time to acknowledge the newcomer's presence. 
She watched as the silt kicked up by her boot entering the water settled down around it.
The refraction of the water's surface made her ankle appear disjointed. 
Her foot twisted around, kicking up yet more silt.\\

``The moons are full tonight,'' Tiffany hummed wistfully, her voice quiet. 
Her eyes were still fixed on the lake's surface, not once did she dare lift them up. 
She did not hear the footsteps growing closer behind her as much as she felt the presence drawing nearer to her.\\

``All four, and still it feels so dark.''\\

The newcomer did not respond. 
A large hunting boot unceremoniously crashed into the water beside her own dainty footwear, a resounding splash rousing the waterfowl asleep in the reeds nearby.
The silt muddied the clear water, and had hardly begun to settle before a large hand settled over Tiffany's shoulder.\\

``Yep, cold. Even through the boot. Come along.''\\

Tiffany did not resist as the man gently guided her back from the lakeshore. 
She was too busy categorising thoughts. 
Important thoughts. 
But one thought stubbornly insisted on taking precedence above all the others.\\

The sum total of buttons reached by the water had reached five.\\

It was a nonsense thought, truly. 
But, counting how many of the soaked buttons dried on the trek back along the forest path was a far more pleasant thought than how wrong this all was.\\

