\chapter{The First Lake (Act 1)}

\section{On another lonely night in Grosbergan, Tiffany Receives her Letter of Acceptance to the Scope Program}

Tiffany was accustomed to the silence, in general.
A night like this, especially, created a familiar expectation for it.
It suited her.
That is what she told herself: she was suited to silence.\\

Anyone else would scoff at that thought, had they truly known her.
Silence was, in fact, something she enjoyed most when it was borne in companionship. 
At times, that companionable silence could also be allowed to give way to endless streams of chatter centred on any sundry subject.\\

Any sundry subject, provided that it was related to Alchemical subjects, the Dragons of Old; Sailtrains were an especially promising new topic, too.
What a conversationalist Tiffany would be if anyone pulled her into those topics.
What a bore, too.
And what if she were incorrect? Or blundered into an offense?
That no offenses could truly be caused regarding these topics was no matter.
Silence suited her best.
She was quite happy to listen most of the time instead.\\

Tiffany was not lonely.
Truly not.
Besides, she was accustomed to silence: it was the best place to be when she needed to get anything done.\\

\textit{``By the light, the crystal binds, so through the night, a spell I shall find...''}
Tiffany's light, lilting voice fully occupied the otherwise abandoned laboratory. 
The shuffling of quartz crystals clinking together as her thin fingers shuffled through the dispensing baskets provided percussion for her little verse.\\

Silence, indeed. 
Perhaps Tiffany defined silence as the absence of noise created from any source that is not yourself.\\

Her fingers closed around a prime candidate for her amplifier: A relatively small rose-quartz with cloudy white banding.
The heft in her palm and the lack of internal cracks at first glance when she held it up to the light told her that this might just be the one.
Tiffany's light boots barely touched the floor as she flitted back to her workbench.
Though, where her steps made little to no noise, the knocking of the stool as she carelessly pulled it from beneath the workbench certainly did.\\

Precariously perched atop the stool, Tiffany grabbed the finelight closer.
Her eyeglass lenses slid down over their frames with a nod of her head.
The fine details of the crystal in her hands came into larger view --- as did an annoyingly red reflection of an escaped curl before her face.
The sensation of the hair secured at the base of her neck slowly pulling from its haphazardly fashioned governance was beginning to feel irksome.
Tiffany was not as bothered with regards to the hair's unruliness as much as she was by its determination to distract her from the object of her thinly reliable attention.\\

The fiery tendril of harrassment blurred to the edge of her vision, becoming a frame for the crystal that was now being inspected thoroughly under the sharp finelight.
Tiffany pooled her focus into the round-tipped wand.
Thin, haphazard cracks and growth lines bloomed into view under the intensifying light.
Quartz was expected to have flaws like these.
None appeared to be too dire, but the scales would have the final say on the crystal's compatibility, and even then the moment of truth will only be when the crystal itself is used.\\

% Tiffany weighs the crystal. Indicate some level of tiredness/distraction by working in some silly mistakes

% Describe the amplification process. Note also the length of time she has been working with some environmental/physical clues.

\section{Fucking hell let's move past the bloody introduction and into something a little more interesting. 
Amid unreliable sailtrains that are hand-waved away by most, Tiffany travels to the Village of Valleyton.
Rowan tongue-in-cheek adivses her to drink the wine there.}

``Sailtrain schedule should remain on-track today, if you would pardon the pun.''\\

Tiffany looked up from securing her suitcase on the rented travel-gourney when a shadow fell over her.
Rowan had appeared as if from nowhere, his frame blocking the glare of Sol Primus from behind.
She squinted her eyes at him, attempting to parse the expression on his face and match it with his speech.
His easy tone belied what could be read as a note of jealousy in his eyes, but Tiffany was accused often enough of reading into things.
She had no need to give it any credence.\\

``If I am lucky. I am more concerned about trusting my luggage to a station-worker in the event the trains do decide to stall before we leave.''\\

``Any baubles valuable enough to be concerned about?'' Rowan chuckled, beginning to rifle through his pockets.\\

``Not valuable, but I would be very upset if I lost my good stockings.'' Tiffany grunted as she forcefully secured the final clasp on the gourney.
``Besides,'' she continued, straightening up with a smile as she patted the deep pockets tied under her overskirt, 
``I have enough material to keep me busy if we \textit{do} find ourselves stranded during an outage.''\\

``Doubt you will need it, no outage has stranded a train, and I doubt it will.''\\

``If Sol Priori is enough to mess with the switchboards, it is enough to mess with a sailtrain's crystal.''\\

Rowan's hearty laugh wobbled her conviction in her statement, but a good humoured smile still clung to her face.
``Here's hoping you have plenty of time to have and sort through your \textit{epiphanies} before you start your work in Valleyton. 
Such valuable brainwaves must be saved for your real work.''\\

Tiffany's face fell just a little at Rowan's response to her statement, and his follow up was not much better. 
She still held on to the possibility that it could be a compliment. 
Although, Tiffany was under no illusions that her theory regarding Sol Priori's encroachment on magical functioning was generally considered a joke at best and a conspiracy theory at worst.\\

Before she could respond, Rowan took her hand and clasped it in his.
She turned it over, and in it was a sealed envelope.

``I am going to be traveling myself, and Prof. Helwyn asked me to keep up with your correspondence and progress nonetheless. 
These are the instructions to reach my mobile teladdress. 
It is a personal line, but I have set it up to forward whatever you send me to Prof. Helwyn too. 
I did not have time to set up the filter on his end for myself. 
If you want to contact me personally, just leave a keyword in your message announcement header.''

[Tiffany is a little too shrewd for this. Even if she is naaive. Is she too shrewd for this? I must figure it out. This feels hella obvious to me.]

Tiffany took the envelope, the outline of a crystal and some other small metal parts [synonym for clearly visible but like, clearly feelable].
An installation kit.
Considerate.\\

``What is the keyword?''\\

Rowan smiled, and a little part of her took a break from her travel-focused thoughts to appreciate the way the humour lit his face.
``Epiphany.''

\subsection{Tiffany Travels to The Scope}

The hiss and splutter of the sail-train's steam outlets announced its arrival before its imposing form did.
Adapted from the old steam trains, the original sail-trains were bulky and wrought large in grey steel.
This carried over into the designs of the sail-trains that were purpose-built to harness solar-sail energy and a heating spell crystal.
Though, their heft was far more reasonable.\\

This train, however, was an older model.
Tiffany squinted at the sight: its coal-chambers, which was previously refurbished to extend the Operator's cabin, was now once again retrofitted to accomodate now-unfamiliar blocks of black coal.\\

Well. 
Take that Rowan.
The average person might not feel that what previously knocked out swathes of switchboards would take a sail-train down, but at least one operator felt it could storngly enough to give up his extra cabin-space for a backup power source.\\

Tiffany was not accustomed to traveling by sail-train often in the last few months.
The last time she went to visit Mountainkeep, most of the older models of the sail-train were either retired or restricted to short-distance journeys.
Having \textit{this} train pull into the station, especially with the extra coal clearly handy, was a sign to Tiffany that the problem of solar-magic's stability had become a real concern.
At least, real enough to the train Operators and the station coordinators that this relic would be pulled out of retirement for a journey of this distance.\\

If the train faltered at any point, it appeared that the coal might be enough to get it into a nearby station.\\

So much for extra time to read, Tiffany sighed to herself.\\

However much this was a soft confirmation of her theories, the beauty of this old train in itself soon overshadowed Tiffany's appreciation of her sitiuation.
This was forged and hammered steel - a hard, cold, reliable vestige of an era when the crystals were yet to fully realise their potential. 

[How long were the crystals in use, and when were they able to become more powerful? 
Does this coincide with technology developing over time?
If solar sails and crystals were in use for a long time, why didn't they hyper-develop?
Crystals were always useful, but their power and interconnected circuitry were only really discovered about ~200 years ago when Sol Priori began growing closer.
So this Sail-Train that Tiffany is looking at is probably something like 150 years old.
Which is reasonable for well-looked-after machinery.]\\

Not that Tiffany was well impressed with the idea of pre-crystal technology slowly making a resurgence in lieu of what could easily been made resilient if it had been properly thought through.
Some acquaintance of the wizarding bent would invariably claim the superiority of inherent energy magical practice.
Of course, when pressed enough, they would stutteringly admit that yes, wands are \textit{technically} a catalyst.
A common rebuttal they would level at this fact would be that, while a catalyst was technically necesssary, the magic was still activated by their internal \textit{intuition}.
Tiffany would invariably laugh at this.\\

[Ah, yes. The undiagnosed ADHD person saying of course ADHD is ridiculous and a fake disorder. I, a \textit{normal} person, act/think/feel like/do that too!]

Whatever magic was activated was just meagre enough to pass as a trick of the fates.
And besides, any claims of "intuitive" or "emotional" connection to the magic was not special.
Every piece of magic, even something as simple as a heating spell, required \textit{intention}.
How else do you activate a welding wand if not by imagining a flame and heating it from yourself?\\

Many other Alchemists [Just change their name to artificers already. This is a well-known word.] did not describe or feel any emotional "connections" to the spells they compiled and activated as she did.
But many would admit that focus and intention were required.
How everyone experienced it, or chose to explain what they experienced for that matter, was completely unique.