\chapter{Preface}
\lettrine{"I}{n the beginning}, there were Stones. Nothing was upon them, and nothing was within them. Through the ether these Stones floated, aimlessly, and without guidance, they continued for a time.
There were four of them, each of a great size, and each could be a dragon's prize.

One by one, each stone was met with a dragon.
The dragons took them up, and bore them upon their backs.
Through the ether each one pressed, flying at speed, to find their perfect nests.

Fate had determined, or misfortune caused, that within this great, empty expanse these four dragons with their Stones should meet.
Each consumed with jealousy, they desired the Stones of the other.
Each overcome with greed, they refused to relinquish their own.

With fire they spat, and with fervour they fought.
The fighting was so vicious that the Stones were each dropped.
Two shattered against each other into fine fragments, and the dragons' fires burned with such eternal heat - that two others were set alight.

The anger and the ferocity of these celestial beings let forth shocks of magic.
The Shattered Stones coalesced into smaller clumps, with some shards setting alight themselves.
The one burning stone remained close, and the other was knocked asunder with a stray tail.
The four dragon's rage continued as their stones floated away, their desires for each other's perfect Stones rendering them useless."


-- So goes the story of the formation of our solar system, according to the children's myths anyway.
They say the tiny burning shards are seen in the night sky from the surface of one of the coalesced fragments that eventually became a home planet.
The whole Stone that burns with eternal heat is, of course, our friendly sun, and her sister, the lesser sun, is the second Stone that was knocked away.

There is a comforting sort of chaos to this story. 
We exist because somehow four dragons just had to know who had the shiniest pebble.
There is another variation of the myth that the dragons returned to the solar system, and, happy with the accidental planet they created, decided to set up shop.
Of course, it also follows that they eventually died, long, long ago.

Dragons did exist, of course. We have found bones. None of the bones are as magical as the myths would have you believe - they have about as much magical energy as the remains of any other living being would.
It is the general consensus that they were some natural species that went extinct.
It is becoming clearer, however, that as the second sun's nearing to our orbit approaches, and as some magical rules seem to bend easier, that at least some people believe the original Four of the Stones may not be so mythical after all. 
At least, they believe it enough to begin searching for them.
\cleardoublepage   % Make sure contents page starts on right-side page