% \lettrine{}{} command typesets a drop cap in the document

% second brace set formats text placed inside as small caps
% (same thing as doing \lettrine{L}\textsc{orem ipsum ...}

\chapter{Lodger}
% We introduce Osthryn, and hint at her draconic origins
% Here we also detail Tiffany's arrival through Osthryn's eyes, and Tiffany's experience of Osthryn's cottage and the town itself from her perspective.

\lettrine{T}{he} twin suns bore down in uncharacteristic heat for a mid-spring day, the clear cloudless skies juxtaposed against a haze of dust yet to be washed down by the first summer rains.
Contentedly Osthryn knelt in the apothecary garden, softly humming away to the rhythmic cut and snip of her shears whilst she gathered \textit{in-universe appropriate plant 1}.
% We want to hint at her draconic and witchy look, but not make it too "obvious"
Her hands glinted bronze in the sun's light when she lifted them to her forehead, a deep emerald hue lighting her eyes as she squinted up at a scratching and scrambling on the cottage's roof.
\vspace{5mm}

Nothing.
\vspace{5mm}

Osthryn scrunched her nose in suspicion. 
Slowly, she raised herself to move closer to the thatch eaves, her grey hair, in a long single plait, swinging past her waist.
She cut a fair figure, her unabashed natural beauty shining through her age.
Her diminuitive stature contrasted with the breadth of her shoulders, practiced and work-worn hands complemented with a stylish arraignment of fine cream linen skirts and an olive green kirtle adorned with bronze threaded embroidery.
The embroidery cascaded down from the collar down to where it bloomed around the circumference of the kirtle's hem. 
The corners of her mouth twitched in amusement, smile lines deepening at the sight of falling dust accompanied with a final set of scrambling sounds.
\vspace{5mm}

With a swiftness that belied her age she snatched the squirming offender from its flight as it attempted to make its escape.
\vspace{5mm}

``Drat-at-at, dat-at-at!!" came the belligerent cry, the sprite's wings still beating furiously.\\
He was no larger than a hummingbird, and as colourful as any one of them. 