% \lettrine{}{} command typesets a drop cap in the document

% second brace set formats text placed inside as small caps
% (same thing as doing \lettrine{L}\textsc{orem ipsum ...}

\chapter{Blood Honey}
% Chapter focusing on the quickly developing dark side of Tiffany and Rowan's dark side from Rowan's perspective. 
% I need to highlight the desparation that Rowan feels to get the job done, to find this important artefact. 
% I need to also acknowledge that he does care for Tiffany, but his selfishness overshadows that.
% In this chapter we have the following scenes:
    % * We witness the push Rowan is under, and we need to get him to think about the 'Spectre' of a future with totally collapsed infrastructure, a future with a botched career, and an immediate future of Tiffany being in trouble if she does not cooperate. (His motivation at the moment feels too extreme. There needs to be less information about the glasswoods in particular, or he needs to be protecting Tiffany to justify either the little info or his `snap' later.)
    % * Rowan pushes Tiffany to divulge information she would have not otherwise done. He needs results, and faster than she is able to give him. He knows this is a betrayal of trust (Thrice: Black Honey)
    % * Rowan bitterly reflects on the `good girl' he is ruining, but the `good girl' he honestly cannot stand. Really dive deep into Estian's scattered headspace here. Superiority and endearment mix in a confusing cocktail. (Grandson: Despicable)
    % * Rowan goes deeper into the forest, looking for evidence of Silovar. He flashes back to the searches he did through Tiffany's office space and bedroom as he catalogs this evidence. All guilt is suppressed in cold calculation. (Grandson: something to hide.)

% Chapter storyline:
    % - This is a forest walk like many before. Romantic tension between him and Tiffany are at a peak. He needs to find the Weeping Willows. He suspects she knows where they are.
    % - He aims to use this walk to 'guide' her hike down routes she never takes. At each attempt, she thwarts him, at each attempt, he fears she is catching 
\lettrine{I}{t was a beautiful evening}. The cheery chorus of forest sounds and the slowly chilling autumn wind caressing the leaves clinging for dear life to their branches 
created a romantic scene that was mostly lost on Rowan tonight, whose thoughts were consumed with the task at hand. 
% Add more detail about how and why he knows about the Henge. This might need to come from a bit more backstory in previous chapters.
% He knows there is a henge, he knows the henge is important, and he knows about a landmark that Tiffany just needs to help him identify.
He had enough data collected from both the observatory and his conversations with Tiffany to build a solid profile: this forest was indeed where the Henge stood.
The one major question for which answers continued to elude him was \textit{what} exactly the Henge contained.
Prof. Helwyn's warning rang loud and clear in his head - if he did not succeed with thoroughly uncovering the Henge before winter, 
the Black Knights will be all too happy to arrange his replacement.
He was not used to missing deadlines. 
\vspace{5mm}
% Intersperse Tiffany's perspective here. See if we can downplay Rowan's thoughts to be less 'obvious'

His fingers instinctively wove between the slender digits of a smaller hand that had slipped its way into his.
He smiled at her as he gave Tiffany's hand a small squeeze. 
He had her right where he needed her to be. 
It was not difficult to appear genuine in his acceptance of her vulnerable gesture, his enjoyment of her company did not need to be faked. 
Her quick and easy conversation spurred on by an excitable mind was as entertaining as it was useful; 
and her soulful, expressive hazel eyes both hoped for and invented all good things in him. 
He sighed internally, if he were a better man, he would have liked to live up to those good things she wished for him to be. 
He was not the better man, he was the best man for the job.
\vspace{5mm}

% Rowan pushes Tiffany to divulge what is behind the stone.
They silently continued hand in hand, the gravel path shifting beneath their feet.
He let Tiffany guide their walk, noting where her eyes rested, and what she avoided.
It was a pattern: every walk they took they would come upon a line of Supress trees, a thin, shallow stream trickling beneath a large knotted oak log, 
and each walk she would turn away. 
\vspace{5mm}

% The following dialogue line will verbatim reference an entry in Tiffany's diary
``The smoking log? Doesn't look very smoldering to me." 
\vspace{5mm}

Tiffany looked up at Rowan, her eyebrows raised for a second as her mouth twitched into an uncertain smile.
His face remained impassive, the well-trained expression of harmless humour setting her at ease.
\vspace{5mm}

``No it isn't, isn't it?"
\newline
``Wanna take a break?" Rowan gestured to the log.
\vspace{5mm}

Not waiting for an answer, he strode over the stream, pausing to lift Tiffany's hand as she hopped over it. 
Discreetly displacing a pebble with a scuff of his shoe, he took the opportunity to steady her with his right hand on the small of her back as she found a wobbly landing.
\vspace{5mm}

``Careful." he chided. 
\newline
``I'll do my best." Tiffany returned with a flirt.
\vspace{5mm}

A quick brush of his fingers against her pulse confirmed her nerves, whether they were from excitement or suspicion, he trusted it was the former.
% More physical stuff here. They sit on the log, Rowan allows her to inch closer to him, and he wraps his arm around her and rests his hand on the log as she leans into him, effectively having her under his arm. This is to convey size difference.
\vspace{5mm}

``Do you like ghost stories?"\\
``...Hmm?"\\
``Got another Epiphany in there?" Rowan grinned, tapping her forehead, allowing himself to enjoy her now decidedly distracted state of mind.\\
Tiffany shook her head with a laugh, ``Not that I would know of."\\
``An Epiphany, or liking ghost stories?"
\vspace{5mm}

Tiffany shot Rowan a look. 
He had to be careful here, he could not push this too far.
\vspace{5mm}

``Do \textit{you} like ghost stories?" She queried, mirth sparkling in her voice.
\vspace{5mm}

Rowan relaxed.
``Oh yeah, I \textit{love} ghost stories. Revenants, poltergeists, vengeful spirits of all kinds...but you,"
He turned to face her, his hand resting on her knee.
"you seem like the `friendly ghost' type, the ghosts that just need some help getting home."\\
``What makes you say that?" Tiffany scoffed, amused.
\vspace{5mm}

Rowan shrugged, animatedly turning towards her, planting his chin on his hand, elbow resting on his crossed knee.\\
``Just a feeling."\\
``Oh yeah?"\\
``Yeah! Sweet girl like you? Pretty sure the only things that could haunt you are the nice ones."\\
``Pretty sure your haunts aren't that bad either, Rowan."
\vspace{5mm}

Rowan chuckled ruefully, ``I wouldn't be so sure about that."\\
It was Tiffany's turn to place a hand on his knee.
\vspace{5mm}

He took the time to look into her eyes, and really study them. 
She was an enigma to him. 
So open, trusting, and vulnerable - it almost drove him mad that she could be as talented as she was. 
Her softness made her stupid, in the worst ways.
Her obsessive perfectionism with her work, however high quality it ended up being, kept her slow and distracted. 
Her openness, curiosity, and helpfulness made the problem worse.
If she were just a bit more shrewd, just a bit more observant, she would not be sitting here with him.
But she was sitting here, and that was good for more reasons than one.
\vspace{5mm}

He did not allow those eyes to wonder for very long what he was thinking about. 
Gently, he gripped the nape of her neck and brought her in for a kiss.
\vspace{5mm}

``Sorry." He whispered as Tiffany's eyes fluttered open, slowly bringing his hands back to his own lap.\\
Tiffany shook her head, stretching to take his hand with a smile.\\
``Don't be."\\
Rowan covered her hand with his free one.\\
``Tell me a ghost story," He whispered, the blinkingly dismissed mist in his eyes having its full effect, "make it a good one."
\vspace{5mm}

% The forest that weeps - Wintersun: Tiffany's perspective switch.