% \lettrine{}{} command typesets a drop cap in the document

% second brace set formats text placed inside as small caps
% (same thing as doing \lettrine{L}\textsc{orem ipsum ...}

\chapter{Locomotion in Brief}
% Locomotion in Brief is the textbook that Tiffany reads while aboard the train.
\lettrine{T}{iffany rocked back and forth} on the balls of her feet, periodically glancing between the station's time-keeper and her own boarding ticket. 
As she would continually insist to both herself and others: she was not a nervous traveller, merely well-prepared.
Her mother had vainly hoped that more experience would eventually temper her need to obsess over the smallest of travel details, yet Tiffany was as meticulous as ever if not more so.
This scrupulosity was further embedded by a recent experience, where, by relying on her travel companions' judgement, she ended up waiting to board a sailtrain at the incorrect platform.
The time she spent stranded while organising a new departure at her own cost had allowed her sufficient room to stew over the matter.
She certainly had no plans to repeat that experience today.
\vspace{1mm}

Right on time, with mere minutes to go, the sailtrain appeared on the rails in the distance.
Clutching her ticket to her chest and tightening her grip on her rolling case, she marvelled once again at the sheer technical beauty of such a vehicle.

The sailtrains were the pinnacle of Alchemical achievement.
Recent advances in `mage sails' and turbine crystals allowed these machines to steadily improve in both mana efficiency and speed.
The newer mage sails were more reactive to the sunlight, enabling more magical energy that was generated by the turbine these sails spun to be trapped in the storage crystals.
The shape of the sailtrains themselves were also more aerodynamic, allowing for smoother acceleration.
This was especially beneficial to the operators - whose mana could now be spared for longer journeys with fewer backup operators required on board, and fewer materials required for continuous spellcasting.

The startling high-pitched screech and grinding of the sailtrain's brakes interrupted her mental reguritation of recent sailtrain developments.
The doors promptly slid open, the clicking and sliding of clockwork powered by solar energy and alchemical engineering quickly dominated by the bustle of passenger exchange.

Far more passengers disembarked than boarded, which suited Tiffany well.
Having shown her ticket to the \textbf{conductor}, and with her rolling case safely stowed above, she took her seat.
Tiffany bemoaned the several layers she had strategically worn to save on luggage-space, the cabin had been left well-warmed by the presence of previous passengers, and the day promised to be rather less wintry than she had hoped for.
Soon enough, the few embarking passengers had taken their seats, and the sailtrain lurched forward and rapidly gained speed.

While the sailtrain was more empty than it would have been for a destination such as the Port-City, the Glasswoods was no unpopular destination.
It was frequented by many visitors of all different purposes and origins.
Some, like herself, were postgraduate students sent on medium-to-long term research projects in either the Observatory, or to study ecosystems and magic interactions in the Glasswoods themselves and surrounding areas.
A good many visitors were tourists and holidaymakers, eager to purchase some household trinkets made of wood harvested from the Glasswood trees and spend some quality family time around the Glasswoods Lake.
In the winter, it was great ice-skating, and in the summer months, was teeming with fish and other wildlife.
Some of these tourists would take exception to the term 'tourist'. 
They were wizards, either of private profession or linked to the university, who firmly believed that Glasswood trees, and specifically \textit{wine} or \textit{whiskey} aged in Glasswood barrels held certain magic-amplification properties.

There was no formal study of this, and Tiffany and other Alchemical students and colleagues were of the opinion that simply the act of practicing magic while slightly buzzed would certainly give the impression to any Wizard that their magical abilities were somehow...\textit{enhanced}.
Tiffany herself found reports of enchanting effects surrounding Glasswood items to be effective marketing, at best.
Certainly there could be \textit{some} traces of magical energy in a Glasswood bead necklace by virtue that all living things contain magical energy to begin with, but amplifying magic with a piece of wood? 
Now that mechanism was unclear, and certainly in her and any other rational magic user's mind, utter nonsense at face value. 

"Sailtrain 4432 eastbound to Glasswood Lake Station, Estimated Time of Arrival is 14:00 [Dragon's Name based weekday. Weekdays are based on the 8 dragons of the creation mythos (4 Major Dragons and 4 Lesser Dragons)]. Meals and refreshments will be made available shortly. Thank you for choosing Twin-Suns for your journey, enjoy the ride!"

The glowing red soundstone faded back out to an ordinary gemstone mounted on Tiffany's table as the announcement ended.
Wistfully, she gazed out of the window, watching as the snowy landscape sped past the traincar, and imagining what her arrival at Glasswoods Lake would have in store for her.
